---
title: "Model_Overview"
date: "`r Sys.Date()`"
output: 
  html_document:
    dev: ragg_png

---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 3000)
```

```{r, include=FALSE}
#options(width = 60)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"', options$max.height)
    )
    hook_output(x, options)
  })
})
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, max.height = '300px', fig.width = 16, fig.height = 8) #fig.show="hold",,

library(data.table)
library(tidyverse)
library(openxlsx)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(gridExtra)
library(conflicted)
library(viridis)
#library(highcharter)

conflict_prefer("filter", "dplyr")
conflict_prefer("first", "dplyr")
conflict_prefer("lag", "dplyr")

source(here("code/dicts.R"))

# # Standard models
models <- readRDS(here("output/final_results/standard_models.RDS")) %>%
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13,
         func = case_when(grepl("^l_edgar_v7", source) ~ "Levels",
                        grepl("^d.l_edgar_v7", source) ~ "Growth rates"))

# # Standard models with weather controls
weather_models <- readRDS(here("output/final_results/weather_calc_dd_models.RDS")) %>%
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13,
         func = case_when(grepl("^l_edgar_v7", source) ~ "Levels",
                        grepl("^d.l_edgar_v7", source) ~ "Growth rates"))

weather_models[-5] %>% group_by(source) %>% summarise(across(everything(), list(all = ~ paste(unique(.x), collapse = ","))))

# Growth rate models with higher p-values
gr_models <- readRDS(here("output/final_results/growth_rate_high_pval.RDS"))

# CFESIS Attempts
cfesis_models <- readRDS(here("output/final_results/cfesis_models_Xtemp_XETS.RDS"))

# Without Luxembourg
# Standard models
standard <- readRDS(here("output/temp/nolux_simpleets.RDS")) %>% 
  rbind(readRDS(here("output/temp/nolux_further_ets_20.RDS"))) %>% 
  # OPTIONAL
  rbind(readRDS(here("output/temp/temporary_ets.RDS"))) %>% 
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13)

# Shares
shares <- readRDS(here("output/temp/shares_noar_nolux.RDS")) %>% 
  rbind(readRDS(here("output/temp/shares_bysource_noar_nolux.RDS"))) %>% 
  rbind(readRDS(here("output/temp/temporary_ets_shares.RDS"))) %>% 
        mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13)

# TEMPORARY FOR KNITTING
temporary_ets <- readRDS(here("output/temp/temporary_ets.RDS"))

```

# Overview: 
All models below were executed with impulse indicator saturation (IIS) enabled and a block size of 20. In order to avoid endless output, where reasonable, we present only the model specifications with all three ETS phase dummies (2005, 2008, 2013), a p-value threshold of 0.01, and spanning 1990-2021.\
 
*Country sample:* EU-15 (not including Luxembourg), United States, Canada, New Zealand, Australia, Japan, Switzerland\

**Updates since 10.11:**\
- Luxembourg excluded\
- CCE estimated with individual FE instead of TWFE\
- ETS dummies interacted with ETS prices\   
- Use low-carbon- , fossil-, renewable-, and source-share of electricity generation as outcome variables\

```{r, include = FALSE, echo = FALSE}

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

dfi <- data %>% 
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2, 
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L), 
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>% 
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))
         
```

```{r, echo = FALSE, include = FALSE}
f <- function(k) {
        step <- k
        function(y) seq(floor(min(y)), ceiling(max(y)), by = step)
}

gen_p <- function(df){
  if(nrow(df) == 0){return("Empty data frame. Model likely not run.")}else{
    for(i in 1:nrow(df)){
      mt <- paste0(df$country_sample[i], " (", df$year_range[i],")", "; p.value: ",df$p_val[i],  "; AR: ",df$ar[i])
      st <- paste0("Formula: ", df$source[i])
    pl <- df %>% 
    slice(i) %>% 
    pull(is) %>% 
    first() %>% 
    plot(zero_line = FALSE) +
        ggtitle(label = mt, subtitle = st) +
  scale_x_continuous(breaks = f(10))
    
    pg <- df %>% 
    slice(i) %>% 
    pull(is) %>% 
    first() %>% 
    plot_grid() +
      ggtitle(label = mt, subtitle = st) 
    
    grid.arrange(pl, pg, ncol = 2)

    print(st)
    print(mt)
    df %>%
    slice(i) %>%
    pull(is) %>%
    first() %>% print()
    }}
}

gen_p_only <- function(df){
  if(nrow(df) == 0){return("Empty data frame. Model likely not run.")}else{
    for(i in 1:nrow(df)){
      mt <- paste0(df$country_sample[i], " (", df$year_range[i],")", "; p.value: ",df$p_val[i],  "; AR: ",df$ar[i])
      st <- paste0("Formula: ", df$source[i])
    pl <- df %>% 
    slice(i) %>% 
    pull(is) %>% 
    first() %>% 
    plot(zero_line = FALSE) +
  scale_x_continuous(breaks = f(10))
    
    print(pl +
        ggtitle(label = mt, subtitle = st))

    print(st)
    print(mt)
    df %>%
    slice(i) %>%
    pull(is) %>%
    first() %>% print()
    }}
}

# Panel of models: indicators to plot generator

convert <- function(mod, modname = character()){
  x <- mod
df <- x$estimateddata
  indicators <- x$isatpanel.result$aux$mX
  indicators <- indicators[,!colnames(indicators) %in% names(df)]
  indicators <- indicators[,!grepl("^id|^time",colnames(indicators))]
  df <- cbind(df,indicators)


    if(is.null(x$isatpanel.result$fit)){
      fitted <- as.numeric(x$isatpanel.result$mean.fit)
    } else {
      fitted <- as.numeric(x$isatpanel.result$fit)
    }

    indicators_df <- cbind(df[,names(df) %in% c("id","time")],indicators)
    varying_vars <- names(indicators_df)[!names(indicators_df)%in% c("id","time","y","fitted")]

    indicators_l <- reshape(indicators_df,
                            varying = varying_vars,
                            idvar = c("id","time"),
                            v.names = "value",
                            timevar = "name",
                            times = varying_vars,
                            direction = "long")

    # introduce facets
    default_facet_name <- "Intercept (IIS, FESIS)"
    indicators_l$facet <- default_facet_name

    # Deal with CSIS within facets
    indicators_l[grepl("\\.csis[0-9]+",indicators_l$name),"value"] <- ifelse(indicators_l[grepl("\\.csis[0-9]+",indicators_l$name),"value"] != 0, 1, 0)
    indicators_l[grepl("\\.csis[0-9]+",indicators_l$name),"facet"] <- paste0("CSIS: ",gsub("\\.csis[0-9]+","",indicators_l[grepl("\\.csis[0-9]+",indicators_l$name),"name"]))

    # Deal with CFESIS within facets
    indicators_l[grepl("\\.cfesis[0-9]+",indicators_l$name),"value"] <- ifelse(indicators_l[grepl("\\.cfesis[0-9]+",indicators_l$name),"value"] != 0, 1, 0)
    indicators_l[grepl("\\.cfesis[0-9]+",indicators_l$name),"facet"] <- paste0("CFESIS: ",gsub("\\.[0-9]+$","",gsub("\\.cfesis[0-9]+","",indicators_l[grepl("\\.cfesis[0-9]+",indicators_l$name),"name"])))

    # Control the order of the facets
    facet_order <- unique(indicators_l$facet)
    facet_order <- c(default_facet_name, facet_order[!facet_order %in% default_facet_name])
    indicators_l$facet <- factor(indicators_l$facet, levels = facet_order)

    indicators_l_merged <- merge(indicators_l,
                                 data.frame(name = names(coef(x$isatpanel.result)),
                                            coef = coef(x$isatpanel.result)),
                                 by = "name", all.x = TRUE)

    indicators_l_merged$effect <-  indicators_l_merged$value*indicators_l_merged$coef

    indicators_toplot <- aggregate(indicators_l_merged$effect, by = list(indicators_l_merged$time, indicators_l_merged$id, indicators_l_merged$facet), function(x){sum(x,na.rm = TRUE)})
    names(indicators_toplot) <- c("time","id","facet","effect")
    indicators_toplot[indicators_toplot$effect == 0,"effect"] <- NA

    indicators_toplot$model <- modname 
    return(indicators_toplot)
}

```

## Model Overview {.tabset}
*Note:* Countries in which no break was detected are excluded from these overview plots.\

### Emissions {.tabset}
#### Overview: Standard Models
```{r, echo = FALSE, fig.height = 16}

mods <- readRDS(here("output/temp/nolux_simpleets.RDS"))

# Standard model
st_mod <- mods %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard")

# Standard controls w/ ETS
st_ets <- mods %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ ETS")

# Standard w/ temperature controls
st_temp <- mods %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ temp")

# Standard w/ temperature controls w/ ETS
st_temp_ets <- mods %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ temp & ETS")

# Temperature & population only
temp_pop <- mods %>% filter(source == "l_edgar_v7 ~ lpop + hdd + cdd" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Temp & Pop Only")

# Temp & Pop only w/ ETS
temp_pop_ets <- mods %>% filter(source == "l_edgar_v7 ~ lpop + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Temp & Pop w/ ETS")

# Standard interacted with ETS price
st_ets_price <- temporary_ets %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ ETS")

# Standard w/ Temp w/ ETS price
st_temp_ets_price <- temporary_ets %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ temp & ETS price")

# Temp & Pop only w/ ETS price
temp_pop_ets_price <- temporary_ets %>% filter(source == "l_edgar_v7 ~ lpop + hdd + cdd + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Temp & Pop w/ ETS price")

comp_lux <- rbind(
  #temp_pop_ets_price,
  temp_pop_ets,
  temp_pop,
  #st_temp_ets_price,
  st_temp_ets,
  st_temp,
  #st_ets_price,
  st_ets,
  st_mod)

comp_lux %>%
  group_by(id) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(id~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 12, angle = 0)) +
      labs(x = NULL, y = NULL, title= "Model Overview: Emissions w/o ETS Price", subtitle = "Specs: p = 0.01; AR = 0")


```

#### Overview: w/ ETS & ETS Price
```{r, echo = FALSE, fig.height = 16}

comp_ets <- rbind(
  temp_pop_ets_price,
  temp_pop_ets,
  #temp_pop,
  st_temp_ets_price,
  st_temp_ets,
  #st_temp,
  st_ets_price,
  st_ets)
  #st_mod)

comp_ets %>%
  group_by(id) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(id~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 12, angle = 0)) +
      labs(x = NULL, y = NULL, title= "Model Overview: Emissions w/ ETS & ETS Prices", subtitle = "Specs: p = 0.01; AR = 0")

```

#### Overview: YFE as TS
```{r, echo = FALSE}

stan <- standard %>% mutate(model = case_when(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq" ~ "Standard",
                           source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd" ~ "Standard w/ Temp",
                           source == "l_edgar_v7 ~ lpop + hdd + cdd" ~ "Pop & Temp",
                           source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" ~ "Standard w/ ETS",
                           source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" ~ "Standard w/ Temp & ETS",
                           source == "l_edgar_v7 ~ lpop + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" ~ "Pop & Temp w/ ETS",
                           source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" ~ "Standard w/ ETS price",
                           source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" ~ "Standard w/ Temp & ETS price",
                           source == "l_edgar_v7 ~ lpop + hdd + cdd + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" ~ "Pop & Temp w/ ETS price")) %>%
                             filter(p_val == 0.01 & year_range == "1990:2021" & ar == 0 & ets_yes %in% c(0,3))

tfe <- tibble()
for(s in 1:nrow(stan)){
  temp <- stan %>% slice(s) %>% pull(is) %>% first
  coefs <- tibble(year = names(coef(temp$isatpanel.result)), coef = coef(temp$isatpanel.result)) %>%
    filter(grepl("time", year)) %>% mutate(year = as.numeric(substr(year, 5,8)))
  tfe <- rbind(tfe, cbind(coefs, model = stan$model[[s]]))
  
}

 x <- models %>% slice(1) %>% pull(is) %>% first
  data.frame(name = names(coef(x$isatpanel.result)), coef = coef(x$isatpanel.result))

tfe %>% tibble %>% ggplot(aes(x = year, y = coef, color = model)) + geom_line() + facet_wrap(~model, scales = "free") +theme_minimal() +theme(legend.position = "none") + labs(x = "Year", y = "Magnitude of Year-Fixed Effects", main = "Year-fixed Effect as Time Series")

```


### Shares: Country Overview {.tabset}
```{r, include = FALSE, echo = FALSE}
org <- shares %>% separate(source, into = c("source","formula"), sep = "[~]") %>%
  mutate(source = trimws(source),
         formula = trimws(formula),
         model = case_when(formula == "lgdp_wb + lpop + lgdp_wb_sq" ~ "Standard",
                           formula == "lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd" ~ "Standard w/ Temp",
                           formula == "lpop + hdd + cdd" ~ "Pop & Temp",
                           formula == "lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" ~ "Standard w/ ETS",
                           formula == "lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" ~ "Standard w/ Temp & ETS",
                           formula == "lpop + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" ~ "Pop & Temp w/ ETS",
                           formula == "lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" ~ "Standard w/ ETS price",
                           formula == "lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" ~ "Standard w/ Temp & ETS price",
                           formula == "lpop + hdd + cdd + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price" ~ "Pop & Temp w/ ETS price")) %>%

                             filter(p_val == 0.01 & year_range == "1990:2021")

converted <- tibble()
for(i in c("low_carbon_share_elec", "renewables_share_elec","fossil_share_elec","solar_share_elec",      "hydro_share_elec","wind_share_elec","nuclear_share_elec","oil_share_elec","coal_share_elec","gas_share_elec")){
  k <- org %>% filter(source == i) %>% nrow
  new <- tibble()
  for(r in 1:k){
    t <- org %>% filter(source == i) %>% slice(r)
    new <- rbind(new, convert(first(t$is), modname = t$model))
  }
  new$indicator <- i
  converted <- rbind(converted, new)
}

# for(n in unique(converted$id)){
#   p <- converted %>% filter(id == i) %>%
#   group_by(indicator) %>%
#   filter(!all(is.na(effect))) %>%
#   ggplot(aes_(x = ~time, y = ~model)) +
#       geom_tile(aes(fill = effect), na.rm = NA) +
#       #scale_fill_viridis_c(na.value = NA) +
#       scale_fill_gradient2(na.value = NA, name = "Effect")+
#       scale_x_continuous(expand = c(0,0)) +
#       scale_y_discrete(limits = rev, expand = c(0,0)) +
#       facet_grid(indicator~.) +
#       theme_bw() +
#       theme(panel.grid = element_blank(),
#             panel.border = element_rect(fill = NA),
#             #panel.spacing.y = unit(0, "lines"),
#             strip.background = element_blank(),
#             axis.text = element_text(size = 10, color = "black"),
#             strip.text.y = element_text(size = 10, angle = 0)) +
#       labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")
# 
# print(p)
# }
```

#### Austria {.tabset}
```{r, echo = FALSE, fig.height = 12}
n <- "Austria"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Belgium {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Belgium"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Germany {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Germany"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Denmark {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Denmark"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Spain {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Spain"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Finland {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Finland"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### France {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "France"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### United Kingdom {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "UnitedKingdom"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Ireland {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Ireland"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Italy {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Italy"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Netherlands {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Netherlands"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Greece {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Greece"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Portugal {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Portugal"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Sweden {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Sweden"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### United States {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "UnitedStates"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Canada {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Canada"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### New Zealand {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "NewZealand"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Australia {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Australia"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Japan {.tabset}
```{r, echo = FALSE,   fig.height = 12}
n <- "Japan"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```

#### Switzerland {.tabset}
```{r, echo = FALSE,  fig.height = 12}
n <- "Switzerland"

p <- converted %>% filter(id == n) %>%
  group_by(indicator) %>%
  filter(!all(is.na(effect))) %>%
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(limits = rev, expand = c(0,0)) +
      facet_grid(indicator~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 10, angle = 0)) +
      labs(x = NULL, y = NULL, title= paste("Model Overview:",n), subtitle = "Specs: p = 0.01; AR = 0")

print(p)

```
