---
title: "Selected Results"
date: "`r Sys.Date()`"
output: 
  html_document:
    dev: ragg_png

---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 3000)
```

```{r, include=FALSE}
#options(width = 60)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"', options$max.height)
    )
    hook_output(x, options)
  })
})
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, max.height = '300px', fig.width = 16, fig.height = 8) #fig.show="hold",,

library(data.table)
library(tidyverse)
library(openxlsx)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(gridExtra)
library(conflicted)
library(viridis)

conflict_prefer("filter", "dplyr")
conflict_prefer("first", "dplyr")
conflict_prefer("lag", "dplyr")

source(here("code/dicts.R"))


# Standard models
models <- readRDS(here("output/final_results/standard_models.RDS")) %>% 
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13,
         func = case_when(grepl("^l_edgar_v7", source) ~ "Levels",
                        grepl("^d.l_edgar_v7", source) ~ "Growth rates"))

# Standard models with weather controls
weather_models <- readRDS(here("output/final_results/weather_calc_dd_models.RDS")) %>% 
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13,
         func = case_when(grepl("^l_edgar_v7", source) ~ "Levels",
                        grepl("^d.l_edgar_v7", source) ~ "Growth rates"))

#weather_models[-5] %>% group_by(source) %>% summarise(across(everything(), list(all = ~ paste(unique(.x), collapse = ",")))) %>% View()

# Growth rate models with higher p-values
gr_models <- readRDS(here("output/final_results/growth_rate_high_pval.RDS"))

# CFESIS Attempts
cfesis_models <- readRDS(here("output/final_results/cfesis_models_Xtemp_XETS.RDS"))

```
# Overview: 
All models below were executed with impulse indicator saturation (IIS) enabled and a block size of 20. In order to avoid endless output, where reasonable, we present only the model specifications with all three ETS phase dummies (2005, 2008, 2013), a p-value threshold of 0.01, and spanning 2019-2021.
 
*Country sample 1:* EU-15, United States, Canada, New Zealand, Australia, Japan, Switzerland     
*Country sample 2:* EU-15 (not including Luxembourg), United States, Canada, New Zealand, Australia, Japan, Switzerland


## Corrections since 18.10 {.tabset}
*Updates:*    
- Updated GDP indicator from current US\$ to constant 2015 US\$ prices   
- Manual calculation of population-weighted HDD (16 degree threshold) and CDD (18 degree threshold) 

```{r, include = FALSE, echo = FALSE}

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

dfi <- data %>% 
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2, 
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L), 
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>% 
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))
         
```

### CDD/HDD calculation {.tabset}
```{r, echo = FALSE, cache = TRUE, warning = FALSE, fig.height=8, fig.width = 10}

df %>% 
  filter(country %in% sel & year >= 1990) %>% 
  select(year, country, cdd, hdd, HDD16dailybypop, CDD18dailybypop) %>% 
  pivot_longer(cols = !c(year, country), names_to = "cat", values_to = "n") %>% 
  mutate(cat = case_when(
    cat == "cdd" ~ "CDD(18) - calculated",
    cat == "hdd" ~ "HDD(16) - calculated",
    cat == "HDD16dailybypop" ~ "HDD(16) - IEA",
    cat == "CDD18dailybypop" ~ "CDD(18) - IEA",
  )) %>% 
  ggplot(aes(x = year, y = n, color = cat)) +
           geom_line(na.rm = TRUE) +
           facet_wrap(vars(country), scales = "free") +
  xlab("Year") +
  ylab("Population-weighted degree days") +
  ggtitle("Comparison of CDD/HDD coverage") +
  scale_color_discrete(name = "Series", 
                       type = c( RColorBrewer::brewer.pal(9, "YlGnBu")[c(5,9)], 
RColorBrewer::brewer.pal(9, "YlOrRd")[c(5,8)]))


```


### GDP correction {.tabset}
```{r, echo = FALSE, cache = TRUE, warning = FALSE, fig.height=8, fig.width = 10}
f <- function(k) {
        step <- k
        function(y) seq(floor(min(y)), ceiling(max(y)), by = step)       
}

df %>% 
  filter(country %in% sel & year >= 1990) %>% 
  ggplot() +
  geom_line(aes(x = year, y = lgdp, color = "GDP Current prices - WB (original)")) +
  geom_line(aes(x = year, y = lgdp_oecd, color = "GDP Constant 2015 prices - OECD")) +
  geom_line(aes(x = year, y = lgdp_wb, color = "GDP Constant 2015 prices - WB"), linetype = "dashed") +
  facet_wrap(vars(country), scales = "free") +
  scale_color_discrete(name = "Series", type = c("#E88471", "#045275", "#DC3977")) +
  xlab("Year") +
  ylab("log US$") +
  ggtitle("Comparison of GDP metrics") +
  scale_x_continuous(breaks = f(10)) +
  theme(legend.position="bottom")
  
```

## Energy shares {.tabset}
### Energy shares {.tabset}
Share of electricity generation by source     
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review

```{r, echo = FALSE, cache = TRUE, warning = FALSE, fig.height=8, fig.width = 10} 

df %>% 
  select(country, year, 
         #low_carbon_share_elec,
         #renewables_share_elec,
         #other_renewables_share_elec,
         #other_renewables_share_elec_exc_biofuel,
         biofuel_share_elec,
         #fossil_share_elec,
         coal_share_elec,
         oil_share_elec,
         gas_share_elec,
         nuclear_share_elec,
         solar_share_elec,
         wind_share_elec,
         hydro_share_elec
         ) %>% 
  filter(country %in% sel & year >=1990) %>% 
  pivot_longer(!c(country, year), names_to = 'source', values_to = 'share') %>%
  ggplot(aes(x = year, y = share, color = source)) +
  geom_line(na.rm = TRUE) +
  facet_wrap(~country, scales = "free")

```

### Electricity generation per source (TWH) {.tabset}
Additional option: Electricity generation by source, measured in terawatt-hours      
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review    
Can be disaggregated by same sources as share data
```{r, echo = FALSE, cache = TRUE, warning = FALSE, fig.height=8, fig.width = 10}

df %>% 
  select(country, year, low_carbon_electricity, renewables_electricity, fossil_electricity) %>% 
  filter(country %in% sel & year >=1990) %>% 
  pivot_longer(!c(country, year), names_to = 'source', values_to = 'elect_twh') %>%
  ggplot(aes(x = year, y = elect_twh, color = source)) +
  geom_line(na.rm = TRUE) +
  facet_wrap(~country, scales = "free")

```


```{r, echo = FALSE, include = FALSE}

gen_p <- function(df){
  if(nrow(df) == 0){return("Empty data frame. Model likely not run.")}else{
    for(i in 1:nrow(df)){
      mt <- paste0(df$country_sample[i], " (", df$year_range[i],")", "; p.value: ",df$p_val[i],  "; AR: ",df$ar[i])
      st <- paste0("Formula: ", df$source[i])
    pl <- df %>% 
    slice(i) %>% 
    pull(is) %>% 
    first() %>% 
    plot(zero_line = FALSE) +
        ggtitle(label = mt, subtitle = st) +
  scale_x_continuous(breaks = f(10))
    
    pg <- df %>% 
    slice(i) %>% 
    pull(is) %>% 
    first() %>% 
    plot_grid() +
      ggtitle(label = mt, subtitle = st) 
    
    grid.arrange(pl, pg, ncol = 2)

    print(st)
    print(mt)
    df %>%
    slice(i) %>%
    pull(is) %>%
    first() %>% print()
    }}
}

gen_p_only <- function(df){
  if(nrow(df) == 0){return("Empty data frame. Model likely not run.")}else{
    for(i in 1:nrow(df)){
      mt <- paste0(df$country_sample[i], " (", df$year_range[i],")", "; p.value: ",df$p_val[i],  "; AR: ",df$ar[i])
      st <- paste0("Formula: ", df$source[i])
    pl <- df %>% 
    slice(i) %>% 
    pull(is) %>% 
    first() %>% 
    plot(zero_line = FALSE) +
  scale_x_continuous(breaks = f(10))
    
    print(pl +
        ggtitle(label = mt, subtitle = st))

    print(st)
    print(mt)
    df %>%
    slice(i) %>%
    pull(is) %>%
    first() %>% print()
    }}
}

# Panel of models: indicators to plot generator

convert <- function(mod, modname = character()){
  x <- mod
df <- x$estimateddata
  indicators <- x$isatpanel.result$aux$mX
  indicators <- indicators[,!colnames(indicators) %in% names(df)]
  indicators <- indicators[,!grepl("^id|^time",colnames(indicators))]
  df <- cbind(df,indicators)


    if(is.null(x$isatpanel.result$fit)){
      fitted <- as.numeric(x$isatpanel.result$mean.fit)
    } else {
      fitted <- as.numeric(x$isatpanel.result$fit)
    }

    indicators_df <- cbind(df[,names(df) %in% c("id","time")],indicators)
    varying_vars <- names(indicators_df)[!names(indicators_df)%in% c("id","time","y","fitted")]

    indicators_l <- reshape(indicators_df,
                            varying = varying_vars,
                            idvar = c("id","time"),
                            v.names = "value",
                            timevar = "name",
                            times = varying_vars,
                            direction = "long")

    # introduce facets
    default_facet_name <- "Intercept (IIS, FESIS)"
    indicators_l$facet <- default_facet_name

    # Deal with CSIS within facets
    indicators_l[grepl("\\.csis[0-9]+",indicators_l$name),"value"] <- ifelse(indicators_l[grepl("\\.csis[0-9]+",indicators_l$name),"value"] != 0, 1, 0)
    indicators_l[grepl("\\.csis[0-9]+",indicators_l$name),"facet"] <- paste0("CSIS: ",gsub("\\.csis[0-9]+","",indicators_l[grepl("\\.csis[0-9]+",indicators_l$name),"name"]))

    # Deal with CFESIS within facets
    indicators_l[grepl("\\.cfesis[0-9]+",indicators_l$name),"value"] <- ifelse(indicators_l[grepl("\\.cfesis[0-9]+",indicators_l$name),"value"] != 0, 1, 0)
    indicators_l[grepl("\\.cfesis[0-9]+",indicators_l$name),"facet"] <- paste0("CFESIS: ",gsub("\\.[0-9]+$","",gsub("\\.cfesis[0-9]+","",indicators_l[grepl("\\.cfesis[0-9]+",indicators_l$name),"name"])))

    # Control the order of the facets
    facet_order <- unique(indicators_l$facet)
    facet_order <- c(default_facet_name, facet_order[!facet_order %in% default_facet_name])
    indicators_l$facet <- factor(indicators_l$facet, levels = facet_order)

    indicators_l_merged <- merge(indicators_l,
                                 data.frame(name = names(coef(x$isatpanel.result)),
                                            coef = coef(x$isatpanel.result)),
                                 by = "name", all.x = TRUE)

    indicators_l_merged$effect <-  indicators_l_merged$value*indicators_l_merged$coef

    indicators_toplot <- aggregate(indicators_l_merged$effect, by = list(indicators_l_merged$time, indicators_l_merged$id, indicators_l_merged$facet), function(x){sum(x,na.rm = TRUE)})
    names(indicators_toplot) <- c("time","id","facet","effect")
    indicators_toplot[indicators_toplot$effect == 0,"effect"] <- NA

    indicators_toplot$model <- modname 
    return(indicators_toplot)
}

# pull_m <- function(df, yr, p, i, a, con = NULL, f = NULL){
#   if(is.null(con) & is.null(f)){
#   df %>%
#     filter(year_range == yr &
#              p_val == p &
#            iis == i &
#            ar == a) %>% pull(is) %>% first()
#   }else{
#     df %>%
#     filter(year_range == yr &
#              p_val == p &
#            iis == i &
#            ar == a &
#              controls == con &
#              func == f) %>% pull(is) %>% first()
#   }
# }
# 
# pull_f <- function(df, src, yr, p, i, a, con = NULL, f = NULL){
#   if(is.null(con) & is.null(f)){
#   df %>%
#     filter(source == src &
#              year_range == yr &
#              p_val == p &
#            iis == i &
#            ar == a) %>% pull(is) %>% first()
#   }else{
#     df %>%
#     filter(source == src &
#              year_range == yr &
#              p_val == p &
#            iis == i &
#            ar == a &
#              controls == con &
#              func == f) %>% pull(is) %>% first()
#   }
# }

######################### Emergency extractors ##############################
# w2000ets %>% pull_f(src = "l_edgar_v7 ~ lgdp + lpop + lgdp_sq + HDD16dailybypop + CDD18dailybypop + EU_ETS_05 + EU_ETS_08 + EU_ETS_13", 
#                     yr = "2000:2021", 
#                     p = 0.001, 
#                     i = TRUE, 
#                     a = 0)
#   #plot
  #plot_grid

# 
# # Simple extract: EU-15+ Standard functional forms (AR1/AR0)
# stand_eu15 %>% filter(b_size == 20) %>% pull_m(df = ., yr = "1990:2021", p = 0.001, i = TRUE, a = 1)
# # Plot
# stand_eu15 %>% 
#   filter(year_range == "1990:2021" &
#           p_val == 0.001 &
#            iis == TRUE &
#            b_size == 20 &
#            ar == 1) %>% gen_p(.)
# 
#  ##############################
# # Simple extract: EU-15+ additional functional forms (AR1/AR0)
# for_models %>% filter(func == "First-diffs" & controls == "Standard Controls") %>%  pull_m(df = ., yr = "1990:2021", p = 0.001, i = TRUE, a = 1)
# for_models %>% 
#   filter(p_val == 0.001 & 
#            ar == 0 & 
#            func == "First-diffs" &
#            controls == "Standard Controls") %>% gen_p(.)
# 
# 
#  ##############################
# # Simple extract: ETS Dummies (AR1/AR0)
# ets %>% filter(ets_08 == TRUE & ets_13 == FALSE) %>% 
#   pull_m(df = .,yr = "1990:2021", p = 0.001, i = TRUE, a = 0, con = "Standard Controls", f = "Levels")
# # Plot
# ets %>% filter(ets_08 == TRUE & 
#                  ets_13 == FALSE &
#                   p_val == 0.001 & 
#                  iis == TRUE & 
#                  ar == 0 &
#                  controls == "Standard Controls" &
#                  func == "Levels") %>% gen_p(.)


```

## Levels {.tabset} 

### Standard Controls {.tabset}

#### 1990-2021 {.tabset}

##### AR = 0 {.tabset}

```{r, echo = FALSE}

models %>% filter(func == "Levels" & year_range == "1990:2021" & ar == 0 & ets_yes == 0 & b_size == 20 & p_val %in% c(0.01, 0.001)) %>% gen_p(.)

```

##### CCE {.tabset}
*Note:* This is a preliminary implementation of the Common Correlated Effects estimator following the method outlined in the code sample provided by Felix a few weeks ago. The manual implementation using *plm* and the dedicated *pcce* function (both from the *plm* package in R) yield identical coefficient estimates to the fourth decimal place.

###### CCE (ERRONEOUS TWFE) {.tabset}

```{r, echo = FALSE, cache = TRUE}

readRDS(here("output/final_results/pcce_models.RDS")) %>% gen_p(.)

```

###### CCE (Individual Effects Only) {.tabset}

```{r, echo = FALSE, cache = TRUE}

readRDS(here("output/final_results/pcce_models_indeffects.RDS")) %>% gen_p(.)

```

##### AR = 1 {.tabset}

```{r, echo = FALSE}

models %>% filter(func == "Levels" & year_range == "1990:2021" & ar == 1 & ets_yes == 0 & b_size == 20 & p_val %in% c(0.01, 0.001)) %>% gen_p(.)

```

##### ETS (all phases) {.tabset}
```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Levels" & year_range == "1990:2021" & ar == 0 & ets_yes == 3 & b_size == 20 & p_val %in% c(0.01, 0.001)) %>% gen_p(.)

```

##### ETS (individual) {.tabset}
```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Levels" & year_range == "1990:2021" & ar == 0 & ets_yes == 1 & b_size == 20 & p_val == 0.001) %>% gen_p(.)

```

##### ETS (pairs) {.tabset}
```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Levels" & year_range == "1990:2021" & ar == 0 & ets_yes == 2 & b_size == 20 & p_val == 0.001) %>% gen_p(.)

```

#### 2000-2021 {.tabset}
##### AR = 0 {.tabset}

```{r, echo = FALSE}

models %>% filter(func == "Levels" & year_range == "2000:2021" & ar == 0 & ets_yes == 0 & b_size == 20 & p_val %in% c(0.01, 0.001)) %>% gen_p(.)

```

##### AR = 1 {.tabset}

```{r, echo = FALSE}

models %>% filter(func == "Levels" & year_range == "2000:2021" & ar == 1 & ets_yes == 0 & b_size == 20 & p_val %in% c(0.01, 0.001)) %>% gen_p(.)

```

##### ETS (all phases) {.tabset}
```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Levels" & year_range == "2000:2021" & ar == 0 & ets_yes == 3 & b_size == 20 & p_val %in% c(0.01, 0.001)) %>% gen_p(.)

```

##### ETS (individual) {.tabset}
```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Levels" & year_range == "2000:2021" & ar == 0 & ets_yes == 1 & b_size == 20 & p_val == 0.001) %>% gen_p(.)

```

##### ETS (pairs) {.tabset}
```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Levels" & year_range == "2000:2021" & ar == 0 & ets_yes == 2 & b_size == 20 & p_val == 0.001) %>% gen_p(.)

```

### w/ Temp Controls {.tabset}

#### 1990-2021 {.tabset}
##### AR = 0 {.tabset}
```{r, echo = FALSE}

weather_models %>% filter(year_range == "1990:2021" & ar == 0 & p_val %in% c(0.01, 0.001) & grepl("lgdp", source) & ets_yes == 0 & b_size == 20) %>% gen_p(.) 

```

##### AR = 1 {.tabset}
```{r, echo = FALSE}

weather_models %>% filter(year_range == "1990:2021" & ar == 1 & p_val %in% c(0.01, 0.001) & grepl("lgdp", source) & ets_yes == 0 & b_size == 20) %>% gen_p(.) 

```

##### ETS (all phases) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "1990:2021" & ar == 0 & p_val %in% c(0.01, 0.001) & grepl("lgdp", source) & ets_yes == 3 & b_size == 20) %>% gen_p(.)

```

##### ETS (individual) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "1990:2021" & ar == 0 & p_val == 0.001 & grepl("lgdp", source) & ets_yes == 1 & b_size == 20) %>% gen_p(.)

```

##### ETS (pairs) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "1990:2021" & ar == 0 & p_val == 0.001 & grepl("lgdp", source) & ets_yes == 2 & b_size == 20) %>% gen_p(.)

```

#### 2000-2021 {.tabset}
##### AR = 0 {.tabset}
```{r, echo = FALSE}

weather_models %>% filter(year_range == "2000:2021" & ar == 0 & p_val %in% c(0.01, 0.001) & grepl("lgdp", source) & ets_yes == 0 & b_size == 20) %>% gen_p(.) 

```

##### AR = 1 {.tabset}
```{r, echo = FALSE}

weather_models %>% filter(year_range == "2000:2021" & ar == 1 & p_val %in% c(0.01, 0.001) & grepl("lgdp", source) & ets_yes == 0 & b_size == 20) %>% gen_p(.) 

```

##### ETS (all phases) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "2000:2021" & ar == 0 & p_val %in% c(0.01, 0.001) & grepl("lgdp", source) & ets_yes == 3 & b_size == 20) %>% gen_p(.)

```

##### ETS (individual) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "2000:2021" & ar == 0 & p_val == 0.001 & grepl("lgdp", source) & ets_yes == 1 & b_size == 20) %>% gen_p(.)

```

##### ETS (pairs) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "2000:2021" & ar == 0 & p_val == 0.001 & grepl("lgdp", source) & ets_yes == 2 & b_size == 20) %>% gen_p(.)

```

### Temp & Pop Only {.tabset}
#### 1990-2021 {.tabset}
##### AR = 0 {.tabset}
```{r, echo = FALSE}

weather_models %>% filter(year_range == "1990:2021" & ar == 0 & p_val %in% c(0.01, 0.001) & !grepl("lgdp", source) & ets_yes == 0 & b_size == 20) %>% gen_p(.) 

```

##### AR = 1 {.tabset}
```{r, echo = FALSE}

weather_models %>% filter(year_range == "1990:2021" & ar == 1 & p_val %in% c(0.01, 0.001) & !grepl("lgdp", source) & ets_yes == 0 & b_size == 20) %>% gen_p(.) 

```

##### ETS (all phases) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "1990:2021" & ar == 0 & p_val %in% c(0.01, 0.001) & !grepl("lgdp", source) & ets_yes == 3 & b_size == 20) %>% gen_p(.)

```

##### ETS (individual) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "1990:2021" & ar == 0 & p_val == 0.001 & !grepl("lgdp", source) & ets_yes == 1 & b_size == 20) %>% gen_p(.)

```

##### ETS (pairs) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "1990:2021" & ar == 0 & p_val == 0.001 & !grepl("lgdp", source) & ets_yes == 2 & b_size == 20) %>% gen_p(.)

```

#### 2000-2021 {.tabset}
##### AR = 0 {.tabset}
```{r, echo = FALSE}

weather_models %>% filter(year_range == "2000:2021" & ar == 0 & p_val %in% c(0.01, 0.001) & !grepl("lgdp", source) & ets_yes == 0 & b_size == 20) %>% gen_p(.) 

```

##### AR = 1 {.tabset}
```{r, echo = FALSE}

weather_models %>% filter(year_range == "2000:2021" & ar == 1 & p_val %in% c(0.01, 0.001) & !grepl("lgdp", source) & ets_yes == 0 & b_size == 20) %>% gen_p(.) 

```

##### ETS (all phases) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "2000:2021" & ar == 0 & p_val %in% c(0.01, 0.001) & !grepl("lgdp", source) & ets_yes == 3 & b_size == 20) %>% gen_p(.)

```

##### ETS (individual) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "2000:2021" & ar == 0 & p_val == 0.001 & !grepl("lgdp", source) & ets_yes == 1 & b_size == 20) %>% gen_p(.)

```

##### ETS (pairs) {.tabset}
```{r, echo = FALSE, cache = TRUE}

weather_models %>% filter(year_range == "2000:2021" & ar == 0 & p_val == 0.001 & !grepl("lgdp", source) & ets_yes == 2 & b_size == 20) %>% gen_p(.)

```


## Growth Rates {.tabset}
*Note: As Moritz mentioned, when looking at growth rates what we understand as "breaks" are represented by the grey impulse lines. I have therefore excluded the plots analogous to the right-hand ones above.*

### AR = 0 {.tabset}
#### p = 0.1 {.tabset}

```{r, echo = FALSE, cache = TRUE}

gr_models %>% filter(year_range == "1990:2021" & b_size == 20 & ar == 0) %>% gen_p_only(.)

```

#### p = 0.05 {.tabset}

```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Growth rates" & year_range == "1990:2021" & p_val == 0.05 & b_size == 20 & ar == 0 & ets_yes == 0) %>% gen_p_only(.)

```

#### p = 0.01 {.tabset}

```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Growth rates" & year_range == "1990:2021" & p_val == 0.01 & b_size == 20 & ar == 0 & ets_yes == 0) %>% gen_p_only(.)

```

#### p = 0.001 {.tabset}

```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Growth rates" & year_range == "1990:2021" & p_val == 0.001 & b_size == 20 & ar == 0 & ets_yes == 0) %>% gen_p_only(.)

```

### AR = 1 {.tabset}
#### p = 0.1 {.tabset}
```{r, echo = FALSE, cache = TRUE}

gr_models %>% filter(year_range == "1990:2021" & b_size == 20 & ar == 1) %>% gen_p_only(.)

```

#### p = 0.05 {.tabset}

```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Growth rates" & year_range == "1990:2021" & p_val == 0.05 & b_size == 20 & ar == 1 & ets_yes == 0) %>% gen_p_only(.)

```

#### p = 0.01 {.tabset}

```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Growth rates" & year_range == "1990:2021" & p_val == 0.01 & b_size == 20 & ar == 1 & ets_yes == 0) %>% gen_p_only(.)

```

#### p = 0.001 {.tabset}

```{r, echo = FALSE, cache = TRUE}

models %>% filter(func == "Growth rates" & year_range == "1990:2021" & p_val == 0.001 & b_size == 20 & ar == 1 & ets_yes == 0) %>% gen_p_only(.)

```


## Testing CFESIS (levels) {.tabset}
Coefficient Fixed Effect Step Indicator Saturation (breaks in the coefficient estimate on the controls for each individual country)   

*Question:* My current interpretation of these steps (denoted in the graph below by the vertical green bars) is potentially a change in emission intensity of GDP (decoupling) and emission intensity of population/people? Unsure if this is accurate. Curious for a discussion on this.

### p = 0.001 {.tabset}

```{r, echo = FALSE, cache = TRUE}
cfesis_models %>% filter(p_val == 0.001) %>% gen_p_only(.)

```

### p = 0.01 {.tabset}

```{r, echo = FALSE, cache = TRUE}
cfesis_models %>% filter(p_val == 0.01) %>% gen_p_only(.)
```


```{r, echo = FALSE, include = FALSE, eval = FALSE}
## Testing TIS (levels) {.tabset}
# Trend indicator saturation. Not sure how to interpret the output here.
# 
# sel = sample of EU15 and selected countries

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

dfi <- data %>% 
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2, 
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L), 
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>% 
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))
         
```


```{r, cache = TRUE, message = FALSE, include = FALSE, eval = FALSE}
### p = 0.001 {.tabset}
tis <- df %>%
      filter(country %in% sel & year >= 1990) %>% 
      isatpanel(data = .,
            formula = "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            tis = TRUE,
            t.pval = 0.001,
            max.block.size = 20)

print(tis)
plot(tis, zero_line = FALSE)

```



```{r, cache = TRUE, message = FALSE, include = FALSE, eval = FALSE}
### p = 0.01 {.tabset}
tis <- df %>%
      filter(country %in% sel & year >= 1990) %>% 
      isatpanel(data = .,
            formula = "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            tis = TRUE,
            t.pval = 0.01,
            max.block.size = 20)

print(tis)
plot(tis, zero_line = FALSE)

```

## Model Overview {.tabset} 
### w/ Luxembourg {.tabset}
```{r, echo = FALSE, fig.height = 16}

# Standard model
st_mod <- models %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard")

# Standard controls w/ ETS
st_ets <- models %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ ETS")

# Standard w/ temperature controls
st_temp <- weather_models %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ temp")

# Standard w/ temperature controls w/ ETS
st_temp_ets <- weather_models %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ temp & ETS")

# Temperature & population only
temp_pop <- weather_models %>% filter(source == "l_edgar_v7 ~ lpop + hdd + cdd" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Temp & Pop Only")

# Temp & Pop only w/ ETS
temp_pop_ets <- weather_models %>% filter(source == "l_edgar_v7 ~ lpop + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Temp & Pop w/ ETS")

# Standard interacted with ETS price
# st_ets_price <- models %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard")

# Growth rates (requires transformation)
# # gr_st

comp_lux <- rbind(temp_pop_ets, temp_pop, st_temp_ets, st_temp, st_ets, st_mod)

ggplot(comp_lux, aes_(x = ~time, y = ~model)) +
    geom_tile(aes(fill = effect), na.rm = NA) +
    #scale_fill_viridis_c(na.value = NA) +
    scale_fill_gradient2(na.value = NA, name = "Effect")+
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_discrete(expand = c(0, 0)) +
    facet_grid(id~.) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          panel.border = element_rect(fill = NA),
          strip.background = element_blank()) +
    labs(x = NULL, y = NULL, title= "Model Overview", subtitle = "Specs: W. Lux; p = 0.01; AR = 0")
```

### w/o Luxembourg {.tabset}
```{r, echo = FALSE, fig.height = 16}

mods <- readRDS(here("output/temp/nolux_simpleets.RDS"))

# Standard model
st_mod <- mods %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard")

# Standard controls w/ ETS
st_ets <- mods %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ ETS")

# Standard w/ temperature controls
st_temp <- mods %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ temp")

# Standard w/ temperature controls w/ ETS
st_temp_ets <- mods %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard w/ temp & ETS")

# Temperature & population only
temp_pop <- mods %>% filter(source == "l_edgar_v7 ~ lpop + hdd + cdd" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Temp & Pop Only")

# Temp & Pop only w/ ETS
temp_pop_ets <- mods %>% filter(source == "l_edgar_v7 ~ lpop + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Temp & Pop w/ ETS")

# Standard interacted with ETS price
# st_ets_price <- models %>% filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq" & p_val == 0.01 & year_range == "1990:2021" & b_size == 20 & ar == 0) %>% pull(is) %>% first %>% convert(., modname = "Standard")

# Growth rates (requires transformation)
# # gr_st

comp_lux <- rbind(temp_pop_ets, temp_pop, st_temp_ets, st_temp, st_ets, st_mod)

comp_lux %>% 
  group_by(id) %>% 
  filter(!all(is.na(effect))) %>% 
  ggplot(aes_(x = ~time, y = ~model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      #scale_fill_viridis_c(na.value = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(expand = c(0,0)) +
      facet_grid(id~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            #panel.spacing.y = unit(0, "lines"),
            strip.background = element_blank(),
            axis.text = element_text(size = 10, color = "black"),
            strip.text.y = element_text(size = 12, angle = 0)) +
      labs(x = NULL, y = NULL, title= "Model Overview", subtitle = "Specs: W.o Lux; p = 0.01; AR = 0")


```


```{r}

nolux <- rbind(readRDS(here("output/temp/nolux_simpleets.RDS")), 
                       readRDS(here("output/temp/nolux_simpleets_bs10_30.RDS")),
                       readRDS(here("output/temp/nolux_further_ets_20.RDS")))
nolux %>% 
  filter(source == "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",
         year_range == "1990:2021",
         b_size == 20,
         p_val == 0.01, 
         ar == 0) %>% gen_p(.)
```

