---
title: "Selected Results"
date: "`r Sys.Date()`"
output: 
  html_document:
    dev: ragg_png

---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 3000)
```

```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, max.height = '300px', fig.width = 16, fig.height = 8) #fig.show="hold",,

library(data.table)
library(tidyverse)
library(openxlsx)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(gridExtra)
library(conflicted)
library(viridis)

conflict_prefer("filter", "dplyr")
conflict_prefer("first", "dplyr")
conflict_prefer("lag", "dplyr")

source(here("code/dicts.R"))


# Without Luxembourg
# Standard models
standard <- readRDS(here("output/temp/nolux_simpleets.RDS")) %>% 
  #rbind(readRDS(here("output/temp/nolux_further_ets_20.RDS"))) %>% 
  #rbind(readRDS(here("output/temp/temporary_ets.RDS"))) %>% 
  rbind(readRDS(here("output/temp/mod_ets_price.RDS"))) %>%
  filter(grepl("l_edgar_v7", source)) %>% 
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13)

# Shares
shares <- readRDS(here("output/temp/shares_noar_nolux.RDS")) %>% 
  rbind(readRDS(here("output/temp/shares_bysource_noar_nolux.RDS"))) %>% 
  rbind(readRDS(here("output/temp/shares_bysource_ar_nolux.RDS"))) %>% 
  rbind(readRDS(here("output/temp/mod_ets_price.RDS"))) %>%
  filter(!grepl("l_edgar_v7", source)) %>% 
  #rbind(readRDS(here("output/temp/temporary_ets_shares.RDS"))) %>% 
        mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13)


```

# Overview:
All models below were executed with impulse indicator saturation (IIS) enabled and a block size of 20. In order to avoid endless output, where reasonable, we present only the model specifications with all three ETS phase dummies (2005, 2008, 2013), a p-value threshold of 0.01, and spanning 1990-2021.\

*Country sample:* EU-15 (not including Luxembourg), United States, Canada, New Zealand, Australia, Japan, Switzerland\

**Updates:**\
- Luxembourg excluded\
- ETS dummies interacted with ETS prices according to specification discussed on 30.11\
- Use low-carbon- , fossil-, renewable-, and source-share of electricity generation as outcome variables\

```{r, include = FALSE, echo = FALSE}

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

dfi <- data %>%
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2,
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L),
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>%
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))

```

## Electricity Share Data {.tabset}

Below, an overview of the data used/available for measuring electricity by source of energy (low-carbon, renewable, fossil, coal, oil, gas, hydro, solar, wind, nuclear).

*Source:* OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review

### Electricity shares {.tabset}

*Unit:* Share of electricity generation by source

#### FF vs. LC
```{r, echo = FALSE, cache = TRUE, warning = FALSE, fig.height=8, fig.width = 10}
df %>%
  mutate(fossil_share_elec = ifelse(is.na(fossil_share_elec), 100 - low_carbon_share_elec, fossil_share_elec)) %>%
  select(country, year,
         low_carbon_share_elec,
         renewables_share_elec,
         fossil_share_elec
         ) %>%
  filter(country %in% sel[sel != "Luxembourg"] & year >=1990) %>%
  pivot_longer(!c(country, year), names_to = 'Source', values_to = 'share') %>%
  ggplot(aes(x = year, y = share, color = Source)) +
  geom_line(na.rm = TRUE) +
  facet_wrap(~country, scales = "free") +
  labs(x = "Year", y = "Share", title = "Share of Total Electricity Generated per Source") +
  theme_bw()
```

#### By Source
```{r, echo = FALSE, cache = TRUE, warning = FALSE, fig.height=8, fig.width = 10}
df %>%
  select(country, year,
         # other_renewables_share_elec,
         # other_renewables_share_elec_exc_biofuel,
         biofuel_share_elec,
         coal_share_elec,
         oil_share_elec,
         gas_share_elec,
         nuclear_share_elec,
         solar_share_elec,
         wind_share_elec,
         hydro_share_elec
         ) %>%
  filter(country %in% sel[sel != "Luxembourg"] & year >=1990) %>%
  pivot_longer(!c(country, year), names_to = 'Source', values_to = 'share') %>%
  ggplot(aes(x = year, y = share, color = Source)) +
  geom_line(na.rm = TRUE) +
  facet_wrap(~country, scales = "free") +
  labs(x = "Year", y = "Share", title = "Share of Total Electricity Generated per Source") +
  theme_bw()

```

### Electricity generation by source (TWh) {.tabset}

*Unit:* Total electricity generated per source, measured in terawatt-hours

#### FF vs. LC
```{r, echo = FALSE, cache = TRUE, warning = FALSE, fig.height=8, fig.width = 10}
df %>%
  select(country, year, low_carbon_electricity, renewables_electricity, fossil_electricity) %>%
  filter(country %in% sel & year >=1990) %>%
  pivot_longer(!c(country, year), names_to = 'Source', values_to = 'elect_twh') %>%
  ggplot(aes(x = year, y = elect_twh, color = Source)) +
  geom_line(na.rm = TRUE) +
  facet_wrap(~country, scales = "free") +
  labs(x = "Year", y = "Electricity Generated (TWh)", title = "Electricity Generated per Source (TWh)")
```

#### By Source
```{r, echo = FALSE, cache = TRUE, warning = FALSE, fig.height=8, fig.width = 10}
df %>%
  select(country, year, oil_electricity, gas_electricity, coal_electricity, solar_electricity, wind_electricity, hydro_electricity, nuclear_electricity) %>%
  filter(country %in% sel & year >=1990) %>%
  pivot_longer(!c(country, year), names_to = 'Source', values_to = 'elect_twh') %>%
  ggplot(aes(x = year, y = elect_twh, color = Source)) +
  geom_line(na.rm = TRUE) +
  facet_wrap(~country, scales = "free") +
  labs(x = "Year", y = "Electricity Generated (TWh)", title = "Electricity Generated per Source (TWh)")

```


```{r, echo = FALSE, include = FALSE}
# Plotting functions

f <- function(k) {
        step <- k
        function(y) seq(floor(min(y)), ceiling(max(y)), by = step)
}

# Arranges result plots (plot and plot_grid) and prints model results
# Option to suppress model results using results = FALSE is required for automatic tabsetting.
gen_p <- function(df, results = TRUE, auto = FALSE){
  if(nrow(df) == 0){return("Empty data frame. Model likely not run.")}else{
    for(i in 1:nrow(df)){
      mt <- paste0(df$country_sample[i], " (", df$year_range[i],")", "; p.value: ",df$p_val[i],  "; AR: ",df$ar[i])
      st <- paste0("Formula: ", df$source[i])
      
    res <- df %>% slice(i) %>% pull(is) %>% first
  
    pl <- res %>% 
      plot(zero_line = FALSE) +
        ggtitle(label = mt, subtitle = st) +
      scale_x_continuous(breaks = f(10))
    
    pg <- res %>%
      plot_grid() +
      ggtitle(label = mt, subtitle = st)
    grid.arrange(pl, pg, ncol = 2)

    if(results == TRUE & auto == FALSE){
        print(st)
        print(mt)
        print(res)
    }else if(results == TRUE & auto == TRUE){
        p <- invisible(capture.output(res$isatpanel.result))
        # Spacing included to trick knitr into reading as verbatim code.
        cat(c("                         \n", 
              "                         \n", 
              paste("                  ", st,'     \n'),
              paste("                  ", mt,'     \n'),
              paste("                  ", p,'     \n')))
      }
    }
  }
}

# Data manipulation function: extracts plot_grid input data from getspanel
# mod = df of models as created above. Minimum requirement is 2 columns (is =  isatpanel object, model = model name)
# na.rm removes countries for which NO model reveals a break/effect
convert <- function(mod){
  if(nrow(mod) == 0){
    print("No models to plot.")
  }else{
    c_mods <- tibble()
    for(m in 1:nrow(mod)){
      mod_name <- mod %>% slice(m) %>% pull(model)
      # Currently, this extracts the data used to build the plot_grid in isatpanel; not ideal
      grid_dat <- mod %>% slice(m) %>% pull(is) %>% first %>% plot_grid %>% ggplot_build
      grid_dat <- grid_dat$plot$data
      grid_dat$model <- mod_name
      c_mods <- rbind(c_mods, grid_dat)
    }
  }
  return(c_mods)
}

plot_comp <- function(mod, panel = "country", na.rm = TRUE){
  tmp <- convert(mod)

  if(panel == "model"){
    tmp <- tmp %>% rename(id = model, model = id)
  }else if(!(panel == "country")){
    print("Error")
    break}else{}

  if(na.rm == TRUE){
    tmp <- tmp %>% group_by(id) %>% filter(!all(is.na(effect)))
    }

  p <- tmp %>% ggplot(aes(x = time, y = model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(expand = c(0,0), limits = rev) +
      facet_grid(id~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            strip.background = element_blank(),
            axis.text = element_text(size = 12, color = "black"),
            strip.text.y = element_text(size = 14, angle = 0)) +
      labs(x = NULL, y = NULL,title= "Model Overview")
  
  print(p)
}

# Similar function as convert but organises w/ respect to multiple outcome variables
convert_mult <- function(mod){
  if(nrow(mod) == 0){
    print("No models to plot.")
  }else{
    c_mods <- tibble()
    for(m in 1:nrow(mod)){
      mod_name <- mod %>% slice(m) %>% pull(model)
      dep_name <- mod %>% slice(m) %>% pull(dep)
      # Currently, this extracts the data used to build the plot_grid in isatpanel
      grid_dat <- mod %>% slice(m) %>% pull(is) %>% first %>% plot_grid %>% ggplot_build
      grid_dat <- grid_dat$plot$data
      grid_dat$model <- mod_name
      grid_dat$dep <- dep_name
      c_mods <- rbind(c_mods, grid_dat)
    }
  }
  return(c_mods)
}

# Pass converted data frame (convert_mult)

plot_country <- function(cmod, country, na.rm = FALSE){
  cmod <- cmod %>% filter(id == country)

  if(na.rm == TRUE){
    cmod <- cmod %>% group_by(dep) %>% filter(!all(is.na(effect)))
  }
  # Replace NAs with 0 value so that cases in which only one model reveals an effect are displayed correctly (limitation of facet_grid)
  cmod %>% mutate(effect = ifelse(is.na(effect), 0, effect)) %>%
    group_by(dep) %>%
    do(gg = {ggplot(., aes(x = time,y = model)) +
        geom_tile(aes(fill = effect)) +
        scale_fill_gradient2(na.value = NA, name = "Effect", oob = scales::squish) +
        scale_x_continuous(expand = c(0,0)) +
        scale_y_discrete(expand = c(0,0), limits = rev) +
        facet_grid(dep~.) +
        theme_bw() +
        theme(panel.grid = element_blank(),
              legend.position = "bottom",
               strip.background = element_blank(),
               axis.text = element_text(size = 12, color = "black"),
               strip.text.y = element_text(size = 12)) +
        labs(x = NULL, y = NULL)
      }) %>%
    .$gg %>% arrangeGrob(grobs = ., ncol = 1) %>% grid.arrange()
}

```

## Emissions: Levels {.tabset}

```{r auto tabs, echo = FALSE, results = 'asis'}

stand_disp <- standard %>%
  mutate(mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>%
  filter(year_range == "1990:2021" & p_val %in% c(0.01, 0.001) & !is.na(ets_spec))

stand_disp %>%
      dplyr::group_split(mod_name) %>%
      purrr::iwalk(.,~{
        name <- unique(.x$mod_name)
        cat('### ', name, '{.tabset}   \n')
          for(e in unique(.x$ets_spec)){
            cat('#### ', e, '{.tabset}   \n')
            for(a in unique(.x$ar)){
            cat('##### AR = ', a, '   \n')
            filter(.x, ets_spec == e & ar == a) %>% gen_p(.,auto = TRUE)
                cat('\n')
                cat('\n')
              }
            cat('\n')
            cat('\n')
            }
        cat('\n')
        cat('\n')
      })


```

## Electricity by Source: Shares {.tabset}
This section only includes the aggregated measures of fossil (coal + gas + oil), renewable (solar + hydro + wind), low carbon (renewable + nuclear). For the model results with the component sources as outcome variables see here INCLUDE LINK!

```{r elec share, echo = FALSE, results='asis'}

shares_disp <- shares %>% separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = str_to_title(gsub("_"," ", gsub("_elec", "", trimws(dep)))),
         formula = trimws(formula),
         mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>% 
                             filter(p_val %in% c(0.01) & year_range == "1990:2021" & dep %in% c("Low Carbon Share", "Renewables Share", "Fossil Share"))

 shares_disp %>% 
   dplyr::group_split(dep) %>%
      purrr::iwalk(.,~{
        ind <- unique(.x$dep)
        cat('### ', ind, '{.tabset}   \n')
        for(n in unique(.x$mod_name)){
           cat('#### ', n, '{.tabset}   \n')
          for(e in unique(.x$ets_spec)){
            cat('##### ', e, '{.tabset}   \n')
            for(a in unique(.x$ar)){
              cat('###### AR = ', a, '   \n')
              filter(.x, mod_name == n & ets_spec == e & ar == a) %>% gen_p(.,auto = TRUE)
              cat('\n')
              cat('\n')
              }
            cat('\n')
            cat('\n')
            }
          cat('\n')
          cat('\n')
          }
        cat('\n')
        cat('\n')
        })

```

## Emissions: Growth Rates {.tabset}
*Note: As Moritz mentioned, when looking at growth rates what we understand as "breaks" are represented by the grey impulse lines. I have therefore excluded the plots analogous to the right-hand ones above.*

```{r, echo = FALSE, results = 'asis'}
readRDS(here("output/temp/growth_rate_standard_nolux.RDS")) %>%
  rbind(readRDS(here("output/temp/growth_rate_temp_nolux.RDS"))) %>%
  mutate(mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp")) %>%
  filter(p_val %in% c(0.01, 0.001) & year_range == "1990:2021") %>%
   dplyr::group_split(mod_name) %>%
      purrr::iwalk(.,~{
        name <- unique(.x$mod_name)
        cat('### ', name, '{.tabset}   \n')
            for(a in unique(.x$ar)){
            cat('#### AR = ', a, '{.tabset}   \n')
              for(p in unique(.x$p_val)){
            cat('##### p = ', p, '   \n')
            filter(.x, ar == a & p_val == p) %>% gen_p(.,auto = TRUE)
                cat('\n')
                cat('\n')
              }
            cat('\n')
            cat('\n')
            }
          cat('\n')
          cat('\n')
      })


```

## Model Overview {.tabset}
*Note:* Countries in which no break was detected are excluded from these overview plots.\

### by country {.tabset}
#### w.o ETS
```{r, echo = FALSE, fig.height = 16}
stand_disp %>% mutate(model = paste(mod_name, ets_spec)) %>% filter(p_val == 0.01 & ets_yes == 0 & ar == 0) %>% plot_comp(.)

```

#### w. ETS
```{r, echo = FALSE, fig.height = 16}

stand_disp %>% mutate(model = paste(mod_name, ets_spec)) %>% filter(p_val == 0.01 & ets_yes == 3 & ar == 0) %>% plot_comp(.)

```

### by model {.tabset}
#### w.o ETS
```{r, echo = FALSE, fig.height = 16}
stand_disp %>% mutate(model = paste(mod_name, ets_spec)) %>% filter(p_val == 0.01 & ets_yes == 0 & ar == 0) %>%  plot_comp(., panel = "model")

```

#### w. ETS
```{r, echo = FALSE, fig.height = 16}

stand_disp %>% mutate(model = paste(mod_name, ets_spec)) %>% filter(p_val == 0.01 & ets_yes == 3 & ar == 0) %>% plot_comp(., panel = "model")

```

### by outcome variable {.tabset}

```{r, echo = FALSE, results = 'asis'}

stand_disp %>% separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = "(Log) Emissions",
         formula = trimws(formula)) %>%
  rbind(shares_disp) %>%
  mutate(model = paste(mod_name, ets_spec)) %>%
  filter(p_val == 0.01 & ar == 0) %>%
  convert_mult %>%
      dplyr::group_split(id) %>%
      purrr::iwalk(.,~{
        c <- unique(.x$id)
        if(!all(is.na(.x$effect))){
          cat('#### ', c, '   \n')
          plot_country(.x, country = c, na.rm = TRUE)
          }
        cat('\n')
        cat('\n')
      })

```


