---
title: "Selected Results: Shares"
date: "`r Sys.Date()`"
output: 
  html_document:
    dev: ragg_png
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 3000)
```

```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, max.height = '300px', fig.width = 16, fig.height = 8) #fig.show="hold",,

rm(list = ls())
library(data.table)
library(tidyverse)
library(openxlsx)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(gridExtra)
library(conflicted)
library(viridis)

conflict_prefer("filter", "dplyr")
conflict_prefer("first", "dplyr")
conflict_prefer("lag", "dplyr")

source(here("code/dicts.R"))

# Standard models
standard <- readRDS(here("output/temp/nolux_simpleets.RDS")) %>% 
  #rbind(readRDS(here("output/temp/nolux_further_ets_20.RDS"))) %>% 
  #rbind(readRDS(here("output/temp/temporary_ets.RDS"))) %>% 
  rbind(readRDS(here("output/temp/mod_ets_price.RDS"))) %>%
  filter(grepl("l_edgar_v7", source)) %>% 
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13)

# Shares
shares <- readRDS(here("output/temp/shares_noar_nolux.RDS")) %>% 
  rbind(readRDS(here("output/temp/shares_bysource_noar_nolux.RDS"))) %>% 
  rbind(readRDS(here("output/temp/shares_bysource_ar_nolux.RDS"))) %>% 
  rbind(readRDS(here("output/temp/mod_ets_price.RDS"))) %>%
  # Incomplete coal, oil, gas, data in previous models, supplemented below
  filter(!grepl("oil", source) & !grepl("coal", source) & !grepl("gas", source), !grepl("nuclear", source)) %>% 
  rbind(filter(readRDS(here("output/temp/supp_share_elec_oil_coal_gas.RDS")), !grepl("fossil", source))) %>% 
  rbind(readRDS(here("output/temp/shares_nuclear_no_zeros.RDS"))) %>% 
  filter(!grepl("l_edgar_v7", source)) %>% 
        mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13)

shares_disp <- shares %>% separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = str_to_title(gsub("_"," ", gsub("_elec", "", trimws(dep)))),
         formula = trimws(formula),
         mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>% 
                             filter(p_val %in% c(0.01) & year_range == "1990:2021") #& dep %in% c("Low Carbon Share", "Renewables Share", "Fossil Share"))


# Logit-transformed shares
logit_shares <- readRDS(here("output/temp/logit_transformed_shares_ff_ren_lc.RDS")) %>%
        mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13) %>% 
  separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = str_to_title(gsub("_"," ", gsub("_elec", "", trimws(dep)))),
         formula = trimws(formula),
         mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>% 
                             filter(p_val %in% c(0.01) & year_range == "1990:2021")


gen_source <- readRDS(here("output/temp/gen_by_source_mods.RDS")) %>%
        mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13) %>% 
  separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = str_to_title(gsub("log ", "", gsub("_"," ", gsub("_electricity", "", trimws(dep))))),
         formula = trimws(formula),
         mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>% 
                             filter(p_val %in% c(0.01) & year_range == "1990:2021")


```


```{r, include = FALSE, echo = FALSE}

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

dfi <- data %>%
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2,
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L),
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>%
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0)) %>% 
  filter(country %in% sel[sel!= "Luxembourg"] & year >= 1990)


iea_elec <- readRDS(here("data/out/IEA_elec_data_by_source.RDS"))

df$coal_electricity[df$country == "New Zealand"] <- iea_elec$sum_value[iea_elec$country == "New Zealand" & iea_elec$code == "coal"]
df$oil_electricity[df$country == "New Zealand"] <- iea_elec$sum_value[iea_elec$country == "New Zealand" & iea_elec$code == "oil"]
df$gas_electricity[df$country == "New Zealand"] <- iea_elec$sum_value[iea_elec$country == "New Zealand" & iea_elec$code == "gas"]

df$coal_electricity[df$country == "Switzerland"] <- iea_elec$sum_value[iea_elec$country == "Switzerland" & iea_elec$code == "coal"]
df$oil_electricity[df$country == "Switzerland"] <- iea_elec$sum_value[iea_elec$country == "Switzerland" & iea_elec$code == "oil"]
df$gas_electricity[df$country == "Switzerland"] <- iea_elec$sum_value[iea_elec$country == "Switzerland" & iea_elec$code == "gas"]

df <- df %>% mutate(coal_share_elec = (coal_electricity/electricity_generation)*100,
         oil_share_elec = (oil_electricity/electricity_generation)*100,
         gas_share_elec = (gas_electricity/electricity_generation)*100)

```


```{r, echo = FALSE, include = FALSE}
# Plotting functions

f <- function(k) {
        step <- k
        function(y) seq(floor(min(y)), ceiling(max(y)), by = step)
}

# Arranges result plots (plot and plot_grid) and prints model results
# Option to suppress model results using results = FALSE is required for automatic tabsetting.
gen_p <- function(df, results = TRUE, auto = FALSE){
  if(nrow(df) == 0){return("Empty data frame. Model likely not run.")}else{
    for(i in 1:nrow(df)){
      mt <- paste0(df$country_sample[i], " (", df$year_range[i],")", "; p.value: ",df$p_val[i],  "; AR: ",df$ar[i])
      st <- paste0("Formula: ", df$source[i])
      
    res <- df %>% slice(i) %>% pull(is) %>% first
  
    pl <- res %>% 
      plot(zero_line = FALSE) +
        ggtitle(label = mt, subtitle = st) +
      scale_x_continuous(breaks = f(10))
    
    pg <- res %>%
      plot_grid() +
      ggtitle(label = mt, subtitle = st)
    grid.arrange(pl, pg, ncol = 2)

    if(results == TRUE & auto == FALSE){
        print(st)
        print(mt)
        print(res)
    }else if(results == TRUE & auto == TRUE){
        p <- invisible(capture.output(res$isatpanel.result))
        # Spacing included to trick knitr into reading as verbatim code.
        cat(c("                         \n", 
              "                         \n", 
              paste("                  ", st,'     \n'),
              paste("                  ", mt,'     \n'),
              paste("                  ", p,'     \n')))
      }
    }
  }
}

# Data manipulation function: extracts plot_grid input data from getspanel
# mod = df of models as created above. Minimum requirement is 2 columns (is =  isatpanel object, model = model name)
# na.rm removes countries for which NO model reveals a break/effect
convert <- function(mod){
  if(nrow(mod) == 0){
    print("No models to plot.")
  }else{
    c_mods <- tibble()
    for(m in 1:nrow(mod)){
      mod_name <- mod %>% slice(m) %>% pull(model)
      # Currently, this extracts the data used to build the plot_grid in isatpanel; not ideal
      grid_dat <- mod %>% slice(m) %>% pull(is) %>% first %>% plot_grid %>% ggplot_build
      grid_dat <- grid_dat$plot$data
      grid_dat$model <- mod_name
      c_mods <- rbind(c_mods, grid_dat)
    }
  }
  return(c_mods)
}

plot_comp <- function(mod, panel = "country", na.rm = TRUE){
  tmp <- convert(mod)

  if(panel == "model"){
    tmp <- tmp %>% rename(id = model, model = id)
  }else if(!(panel == "country")){
    print("Error")
    break}else{}

  if(na.rm == TRUE){
    tmp <- tmp %>% group_by(id) %>% filter(!all(is.na(effect)))
    }

  p <- tmp %>% ggplot(aes(x = time, y = model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(expand = c(0,0), limits = rev) +
      facet_grid(id~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            strip.background = element_blank(),
            axis.text = element_text(size = 12, color = "black"),
            strip.text.y = element_text(size = 14, angle = 0)) +
      labs(x = NULL, y = NULL,title= "Model Overview")
  
  print(p)
}

# Similar function as convert but organises w/ respect to multiple outcome variables
convert_mult <- function(mod){
  if(nrow(mod) == 0){
    print("No models to plot.")
  }else{
    c_mods <- tibble()
    for(m in 1:nrow(mod)){
      mod_name <- mod %>% slice(m) %>% pull(model)
      dep_name <- mod %>% slice(m) %>% pull(dep)
      # Currently, this extracts the data used to build the plot_grid in isatpanel
      grid_dat <- mod %>% slice(m) %>% pull(is) %>% first %>% plot_grid %>% ggplot_build
      grid_dat <- grid_dat$plot$data
      grid_dat$model <- mod_name
      grid_dat$dep <- dep_name
      c_mods <- rbind(c_mods, grid_dat)
    }
  }
  return(c_mods)
}

# Pass converted data frame (convert_mult)

plot_country <- function(cmod, country, na.rm = FALSE){
  cmod <- cmod %>% filter(id == country)

  if(na.rm == TRUE){
    cmod <- cmod %>% group_by(dep) %>% filter(!all(is.na(effect)))
  }
  # Replace NAs with 0 value so that cases in which only one model reveals an effect are displayed correctly (limitation of facet_grid)
  cmod %>% mutate(effect = ifelse(is.na(effect), 0, effect)) %>%
    group_by(dep) %>%
    do(gg = {ggplot(., aes(x = time,y = model)) +
        geom_tile(aes(fill = effect)) +
        scale_fill_gradient2(na.value = NA, name = "Effect", oob = scales::squish) +
        scale_x_continuous(expand = c(0,0)) +
        scale_y_discrete(expand = c(0,0), limits = rev) +
        facet_grid(dep~.) +
        theme_bw() +
        theme(panel.grid = element_blank(),
              legend.position = "bottom",
               strip.background = element_blank(),
               axis.text = element_text(size = 12, color = "black"),
               strip.text.y = element_text(size = 12)) +
        labs(x = NULL, y = NULL)
      }) %>%
    .$gg %>% arrangeGrob(grobs = ., ncol = 1) %>% grid.arrange()
}

```

## Electricity by Source: Shares {.tabset}

```{r, echo = FALSE, results='asis'}

stand_disp <- standard %>%
  mutate(mod_name = case_when(grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
         grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp",
         !grepl("cdd", source) ~ "Standard Controls"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>%
  filter(year_range == "1990:2021" & p_val == 0.01 & !is.na(ets_spec)) %>% 
  separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = "Emissions",
         formula = trimws(formula))

ov_disp <- stand_disp %>%
  rbind(shares_disp) %>%
  mutate(model = paste(mod_name, ets_spec)) %>%
  filter(p_val == 0.01)


ov_disp %>%
  filter(mod_name == "Standard Controls w. Temp" & ets_spec %in% c("w.o ETS", "w. ETS price") & !(dep %in% c("Low Carbon Share", "Renewables Share", "Fossil Share"))) %>% 
   dplyr::group_split(dep) %>%
      purrr::iwalk(.,~{
        ind <- unique(.x$dep)
        cat('### ', ind, '{.tabset}   \n')
        # for(n in unique(.x$mod_name)){
        #    cat('#### ', n, '{.tabset}   \n')
          for(e in unique(.x$ets_spec)){
            cat('#### ', e, '{.tabset}   \n')
            for(a in unique(.x$ar)){
              cat('##### AR = ', a, '   \n')
              filter(.x, ets_spec == e & ar == a) %>% gen_p(.,auto = TRUE)
              cat('\n')
              cat('\n')
              }
            cat('\n')
            cat('\n')
            }
          cat('\n')
          cat('\n')
          }
        # cat('\n')
        # cat('\n')
        # }
        )

```


### Model Overview {.tabset}
*Note:* Countries in which no break was detected are excluded from these overview plots.\

#### Overview by country {.tabset}

```{r, echo = FALSE, results = 'asis', fig.height = 16}

ov_disp %>%
   filter(ar == 0 & !(dep %in% c("Low Carbon Share", "Renewables Share", "Fossil Share"))) %>% 
   dplyr::group_split(dep) %>%
      purrr::iwalk(.,~{
        ind <- unique(.x$dep)
        cat('##### ', ind, '{.tabset}   \n')
        for(e in unique(.x$ets_yes)){
            e_title <- ifelse(e == 3, "w. ETS", "w.o ETS")
            cat('###### ', e_title, '   \n')
              .x %>% filter(ets_yes == e) %>% plot_comp(.)
            cat('\n')
            cat('\n')
        }
        cat('\n')
        cat('\n')
      })

```

#### Country overview by outcome variable {.tabset}

```{r, echo = FALSE, results = 'asis', fig.height = 16}


ov_disp %>%
  filter(ar == 0 & !(dep %in% c("Low Carbon Share", "Renewables Share", "Fossil Share"))) %>%
  convert_mult %>%
      dplyr::group_split(id) %>%
      purrr::iwalk(.,~{
        c <- unique(.x$id)
        if(!all(is.na(.x$effect))){
          cat('##### ', c, '   \n')
          plot_country(.x, country = c, na.rm = TRUE)
          }
        cat('\n')
        cat('\n')
      })

```

<!-- ## Electricity by Source: Logit-transformed Shares (Selected) {.tabset} -->

<!-- ```{r elec share logit, echo = FALSE, results='asis'} -->

<!-- shares_disp %>%  -->
<!--   filter(dep %in% c("Fossil Share", "Low Carbon Share", "Renewables Share")) %>%  -->
<!--   rbind(logit_shares) %>%  -->
<!--   mutate(cat = case_when(grepl("Fossil", dep) ~ "Fossil", -->
<!--                          grepl("Low Carbon", dep) ~ "Low Carbon", -->
<!--                          grepl("Renewable", dep) ~ "Renewable"), -->
<!--          type = case_when(grepl("Logit", dep) ~ "Logit Share", -->
<!--                           !grepl("Logit", dep) ~ "Share")) %>%  -->
<!--   mutate(model = paste(mod_name, ets_spec)) %>% -->
<!--   filter(mod_name == "Standard Controls w. Temp" & ets_spec %in% c("w.o ETS", "w. ETS price")) %>%  -->
<!--    dplyr::group_split(cat) %>% -->
<!--       purrr::iwalk(.,~{ -->
<!--         ind <- unique(.x$cat) -->
<!--         cat('### ', ind, '{.tabset}   \n') -->
<!--         for(n in unique(.x$type)){ -->
<!--            cat('#### ', n, '{.tabset}   \n') -->
<!--           for(e in unique(.x$ets_spec)){ -->
<!--             cat('##### ', e, '{.tabset}   \n') -->
<!--             for(a in unique(.x$ar)){ -->
<!--               cat('###### AR = ', a, '   \n') -->
<!--               filter(.x, type == n & ets_spec == e & ar == a) %>% gen_p(.,auto = TRUE) -->
<!--               cat('\n') -->
<!--               cat('\n') -->
<!--               } -->
<!--             cat('\n') -->
<!--             cat('\n') -->
<!--             } -->
<!--           cat('\n') -->
<!--           cat('\n') -->
<!--           } -->
<!--         cat('\n') -->
<!--         cat('\n') -->
<!--         } -->
<!--         ) -->

<!-- ``` -->


## Electricity by Source: Levels {.tabset}

```{r, echo = FALSE, results='asis'}


lev_disp <- gen_source %>%
  mutate(model = paste(mod_name, ets_spec)) %>%
  filter(p_val == 0.01)

lev_disp %>%
  filter(mod_name == "Standard Controls w. Temp" & ets_spec %in% c("w.o ETS", "w. ETS price")) %>% 
   dplyr::group_split(dep) %>%
      purrr::iwalk(.,~{
        ind <- unique(.x$dep)
        cat('### ', ind, '{.tabset}   \n')
        for(n in unique(.x$mod_name)){
           cat('#### ', n, '{.tabset}   \n')
          for(e in unique(.x$ets_spec)){
            cat('##### ', e, '{.tabset}   \n')
            for(a in unique(.x$ar)){
              cat('###### AR = ', a, '   \n')
              filter(.x, mod_name == n & ets_spec == e & ar == a) %>% gen_p(.,auto = TRUE)
              cat('\n')
              cat('\n')
              }
            cat('\n')
            cat('\n')
            }
          cat('\n')
          cat('\n')
          }
        cat('\n')
        cat('\n')
        })

```

### Model Overview {.tabset}
*Note:* Countries in which no break was detected are excluded from these overview plots.\

#### Overview by country {.tabset}

```{r, echo = FALSE, results = 'asis', fig.height = 16}

lev_disp %>%
   filter(ar == 0) %>% 
   dplyr::group_split(dep) %>%
      purrr::iwalk(.,~{
        ind <- unique(.x$dep)
        cat('##### ', ind, '{.tabset}   \n')
        for(e in unique(.x$ets_yes)){
            e_title <- ifelse(e == 3, "w. ETS", "w.o ETS")
            cat('###### ', e_title, '   \n')
              .x %>% filter(ets_yes == e) %>% plot_comp(.)
            cat('\n')
            cat('\n')
        }
        cat('\n')
        cat('\n')
      })

```

#### Country overview by outcome variable {.tabset}

```{r, echo = FALSE, results = 'asis', fig.height = 16}


lev_disp %>%
  filter(ar == 0) %>%
  convert_mult %>%
      dplyr::group_split(id) %>%
      purrr::iwalk(.,~{
        c <- unique(.x$id)
        if(!all(is.na(.x$effect))){
          cat('##### ', c, '   \n')
          plot_country(.x, country = c, na.rm = TRUE)
          }
        cat('\n')
        cat('\n')
      })

```


