---
title: "Streamlined_Results"
author: "Ebba Mark"
date: "`r Sys.Date()`"
output: 
  html_document:
    dev: ragg_png

---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 3000)
```

```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, max.height = '300px', fig.width = 16, fig.height = 8) #fig.show="hold",,

library(data.table)
library(tidyverse)
library(openxlsx)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(grid)
library(gridExtra)
library(conflicted)
library(viridis)

conflict_prefer("filter", "dplyr")
conflict_prefer("first", "dplyr")
conflict_prefer("lag", "dplyr")

source(here("code/dicts.R"))


# Without Luxembourg
# Standard models
standard <- readRDS(here("output/temp/nolux_simpleets.RDS")) %>% 
  #rbind(readRDS(here("output/temp/nolux_further_ets_20.RDS"))) %>% 
  #rbind(readRDS(here("output/temp/temporary_ets.RDS"))) %>% 
  rbind(readRDS(here("output/temp/mod_ets_price.RDS"))) %>%
  filter(grepl("l_edgar_v7", source)) %>% 
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13)

# Production models
prod <- readRDS(here("output/temp/production_data_models.RDS")) %>% 
  rbind(readRDS(here("output/temp/imports_export_models.RDS"))) %>% 
  mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13) %>% 
  separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = str_to_title(gsub("log ", "", gsub("_"," ", gsub("_electricity", "", trimws(dep))))),
         formula = trimws(formula),
         mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>% 
                             filter(p_val %in% c(0.01) & year_range == "1990:2021")

# Shares
shares <- readRDS(here("output/temp/shares_noar_nolux.RDS")) %>% 
  rbind(readRDS(here("output/temp/shares_bysource_noar_nolux.RDS"))) %>% 
  rbind(readRDS(here("output/temp/shares_bysource_ar_nolux.RDS"))) %>% 
  rbind(readRDS(here("output/temp/mod_ets_price.RDS"))) %>%
  # Incomplete coal, oil, gas, data in previous models, supplemented below
  filter(!grepl("oil", source) & !grepl("coal", source) & !grepl("gas", source), !grepl("nuclear", source)) %>% 
  rbind(filter(readRDS(here("output/temp/supp_share_elec_oil_coal_gas.RDS")), !grepl("fossil", source))) %>% 
  rbind(readRDS(here("output/temp/shares_nuclear_no_zeros.RDS"))) %>% 
  filter(!grepl("l_edgar_v7", source)) %>% 
        mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13)

shares_disp <- shares %>% separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = str_to_title(gsub("_"," ", gsub("_elec", "", trimws(dep)))),
         formula = trimws(formula),
         mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>% 
                             filter(p_val %in% c(0.01) & year_range == "1990:2021") #& dep %in% c("Low Carbon Share", "Renewables Share", "Fossil Share"))

# Logit-transformed shares
logit_shares <- readRDS(here("output/temp/logit_transformed_shares_ff_ren_lc.RDS")) %>%
        mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13) %>% 
  separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = str_to_title(gsub("_"," ", gsub("_elec", "", trimws(dep)))),
         formula = trimws(formula),
         mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>% 
                             filter(p_val %in% c(0.01) & year_range == "1990:2021")

gen_source <- readRDS(here("output/temp/gen_by_source_mods.RDS")) %>%
        mutate(ets_05 = ifelse(grepl("EU_ETS_05", source), 1, 0),
         ets_08 = ifelse(grepl("EU_ETS_08", source), 1, 0),
         ets_13 = ifelse(grepl("EU_ETS_13", source), 1, 0),
         ets_yes = ets_05 + ets_08 + ets_13) %>% 
  separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = str_to_title(gsub("log ", "", gsub("_"," ", gsub("_electricity", "", trimws(dep))))),
         formula = trimws(formula),
         mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>% 
                             filter(p_val %in% c(0.01) & year_range == "1990:2021")

```


# Streamlined Overview:
All models below were executed with impulse indicator saturation (IIS) enabled and a block size of 20. Results are displayed for our selected baseline model: with GDP, population, weather controls, all three ETS phase dummies (2005, 2008, 2013), a p-value threshold of 0.01, and spanning 1990-2021.\

*Country sample:* EU-15 (excluding Luxembourg), United States, Canada, New Zealand, Australia, Japan, Switzerland\
For certain specifications (coal, nuclear, exports, imports) countries with significant level of zero values have been removed.\

"Channels" refer to our indicated "demand/generation" and "technology" channels which distinguish between changes in electricity consumption/behavior (demand, generation, exports/imports) and electricity sources. For clarity, detected breaks are represented by black lines in the comparison plots.\

```{r, echo = FALSE, include = FALSE}
# Plotting functions

f <- function(k) {
        step <- k
        function(y) seq(floor(min(y)), ceiling(max(y)), by = step)
}

# Arranges result plots (plot and plot_grid) and prints model results
# Option to suppress model results using results = FALSE is required for automatic tabsetting.
gen_p <- function(df, results = TRUE, auto = FALSE){
  if(nrow(df) == 0){return("Empty data frame. Model likely not run.")}else{
    for(i in 1:nrow(df)){
      mt <- paste0(df$country_sample[i], " (", df$year_range[i],")", "; p.value: ",df$p_val[i],  "; AR: ",df$ar[i])
      st <- paste0("Formula: ", df$source[i])
      
    res <- df %>% slice(i) %>% pull(is) %>% first
  
    pl <- res %>% 
      plot(zero_line = FALSE) +
        ggtitle(label = mt, subtitle = st) +
      scale_x_continuous(breaks = f(10))
    
    pg <- res %>%
      plot_grid() +
      ggtitle(label = mt, subtitle = st)
    grid.arrange(pl, pg, ncol = 2)

    if(results == TRUE & auto == FALSE){
        print(st)
        print(mt)
        print(res)
    }else if(results == TRUE & auto == TRUE){
        p <- invisible(capture.output(res$isatpanel.result))
        # Spacing included to trick knitr into reading as verbatim code.
        cat(c("                         \n", 
              "                         \n", 
              paste("                  ", st,'     \n'),
              paste("                  ", mt,'     \n'),
              paste("                  ", p,'     \n')))
      }
    }
  }
}

# Data manipulation function: extracts plot_grid input data from getspanel
# mod = df of models as created above. Minimum requirement is 2 columns (is =  isatpanel object, model = model name)
# na.rm removes countries for which NO model reveals a break/effect
convert <- function(mod){
  if(nrow(mod) == 0){
    print("No models to plot.")
  }else{
    c_mods <- tibble()
    for(m in 1:nrow(mod)){
      mod_name <- mod %>% slice(m) %>% pull(model)
      # Currently, this extracts the data used to build the plot_grid in isatpanel; not ideal
      grid_dat <- mod %>% slice(m) %>% pull(is) %>% first %>% plot_grid %>% ggplot_build
      grid_dat <- grid_dat$plot$data
      grid_dat$model <- mod_name
      c_mods <- rbind(c_mods, grid_dat)
    }
  }
  return(c_mods)
}

plot_comp <- function(mod, panel = "country", na.rm = TRUE, sign = NULL){
  tmp <- convert(mod)

  if(panel == "model"){
    tmp <- tmp %>% rename(id = model, model = id)
  }else if(!(panel == "country")){
    print("Error")
    break}else{}

  if(na.rm == TRUE){
    tmp <- tmp %>% group_by(id) %>% filter(!all(is.na(effect)))
  }
  if(sign == "pos"){
    tmp <- tmp %>% group_by(id) %>% filter(any(effect > 0))
    
  }else if(sign == "neg") { tmp <- tmp %>% group_by(id) %>% filter(any(effect < 0))}

  p <- tmp %>% ggplot(aes(x = time, y = model)) +
      geom_tile(aes(fill = effect), na.rm = NA) +
      scale_fill_gradient2(na.value = NA, name = "Effect")+
      scale_x_continuous(expand = c(0,0)) +
      scale_y_discrete(expand = c(0,0), limits = rev) +
      facet_grid(id~.) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.border = element_rect(fill = NA),
            strip.background = element_blank(),
            axis.text = element_text(size = 12, color = "black"),
            strip.text.y = element_text(size = 14, angle = 0)) +
      labs(x = NULL, y = NULL,title= "Model Overview")
  
  print(p)
}

# Similar function as convert but organises w/ respect to multiple outcome variables
convert_mult <- function(mod){
  if(nrow(mod) == 0){
    print("No models to plot.")
  }else{
    c_mods <- tibble()
    for(m in 1:nrow(mod)){
      mod_name <- mod %>% slice(m) %>% pull(model)
      dep_name <- mod %>% slice(m) %>% pull(dep)
      # Currently, this extracts the data used to build the plot_grid in isatpanel
      grid_dat <- mod %>% slice(m) %>% pull(is) %>% first %>% plot_grid %>% ggplot_build
      grid_dat <- grid_dat$plot$data
      grid_dat$model <- mod_name
      grid_dat$dep <- dep_name
      c_mods <- rbind(c_mods, grid_dat)
    }
  }
  return(c_mods)
}

# Pass converted data frame (convert_mult)

plot_country <- function(cmod, country, bs = list(), na.rm = FALSE){
  cmod <- cmod %>% filter(id == country)

  if(na.rm == TRUE){
    cmod <- cmod %>% group_by(dep) %>% filter(!all(is.na(effect)))
  }
  if(nrow(cmod)== 0){return()}
  # Replace NAs with 0 value so that cases in which only one model reveals an effect are displayed correctly (limitation of facet_grid)
  cmod %>% mutate(effect = ifelse(is.na(effect), 0, effect)) %>%
    group_by(dep) %>%
    do(gg = {ggplot(., aes(x = time, y = model)) +
        geom_tile(aes(fill = effect)) +
        scale_fill_gradient2(na.value = NA, name = "Effect", oob = scales::squish) +
        scale_x_continuous(expand = c(0,0)) +
        scale_y_discrete(expand = c(0,0), limits = rev) +
        geom_vline(xintercept = bs) +
        facet_grid(dep~.) +
        theme_bw() +
        theme(panel.grid = element_blank(),
              legend.position = "bottom",
               strip.background = element_blank(),
               axis.text = element_blank(), #element_text(size = 12, color = "black"),
               strip.text.y = element_text(size = 12)) +
        labs(x = NULL, y = NULL)
      }) %>%
    .$gg %>% arrangeGrob(grobs = ., ncol = 1) %>% grid.arrange()
}

get_breaks <- function(mods, sign = "all"){
  breaks <- c()
  for(s in 1:nrow(mods)){
  breaks <- mods %>% slice(s) %>% pull(is) %>% first %>% break_uncertainty(.) %>% rbind(breaks, .)}
  if(sign == "neg"){
    neg_b <- breaks %>% filter(coef < 0) %>% pull(id) %>% unique
    return(neg_b)
  }else if(sign == "pos"){
    pos_b <- breaks %>% filter(coef > 0) %>% pull(id) %>% unique
    return(pos_b)
  }else if(sign == "all"){
    all_b <- breaks %>% pull(id) %>% unique
    return(all_b)}
}

```

## Emissions: All detected breaks {.tabset}

```{r auto tabs, echo = FALSE, results = 'asis'}

stand_disp <- standard %>%
  mutate(mod_name = case_when(!grepl("cdd", source) ~ "Standard Controls",
                              grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
                              grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>%
  filter(year_range == "1990:2021" & !is.na(ets_spec))

stand_disp %>%
  filter(mod_name == "Standard Controls w. Temp" & ets_spec %in% c("w. ETS") & ar == 0 & p_val < 0.05) %>% 
  mutate(model = paste("p=",p_val)) %>% plot_comp(., sign = "all")
```


## Negative Emissions Breaks  {.tabset}
*Note:* Countries in which no break was detected are excluded from these overview plots.\

### Emissions {.tabset}

```{r, echo = FALSE, fig.height = 14}

stand_forms <- stand_disp %>%
  filter(mod_name == "Standard Controls w. Temp" & ets_spec== "w. ETS" & ar == 0 & p_val < 0.05) %>% 
  mutate(model = paste("p=",p_val))

stand_forms %>% plot_comp(., sign = "neg")

```

### Channels {.tabset}
```{r, echo = FALSE, include = FALSE}

dem_disp <- prod %>%
  mutate(model = paste(mod_name, ets_spec)) %>% 
  filter(p_val == 0.01 & model == "Standard Controls w. Temp w. ETS" & ar == 0) 

lev_disp <- gen_source %>%
  mutate(model = paste(mod_name, ets_spec)) %>%
  filter(p_val == 0.01 & ar == 0 & model == "Standard Controls w. Temp w. ETS") 

ov_disp <- standard %>%
  mutate(mod_name = case_when(grepl("cdd", source) & grepl("lgdp", source) ~ "Standard Controls w. Temp",
         grepl("cdd", source) & !grepl("lgdp", source) ~ "Pop w. Temp",
         !grepl("cdd", source) ~ "Standard Controls"),
         ets_spec = case_when(ets_yes == 0 ~ "w.o ETS",
                              ets_yes == 3 & grepl("ets_price", source) ~ "w. ETS price",
                              ets_yes == 3 & !grepl("ets_price", source) ~ "w. ETS")) %>%
  filter(year_range == "1990:2021" & p_val == 0.01 & !is.na(ets_spec)) %>% 
  separate(source, into = c("dep","formula"), sep = "[~]", remove = FALSE) %>%
  mutate(dep = "Emissions",
         formula = trimws(formula)) %>%
  rbind(shares_disp) %>%
  mutate(model = paste(mod_name, ets_spec)) %>%
  filter(p_val == 0.01) %>% 
  filter(ar == 0 & !(dep %in% c("Low Carbon Share", "Renewables Share", "Fossil Share", "Emissions")) & model == "Standard Controls w. Temp w. ETS")

nb <- stand_disp %>%
  filter(mod_name == "Standard Controls w. Temp" & ets_spec== "w. ETS" & ar == 0 & p_val == 0.01) %>% 
  pull(is) %>% first %>% break_uncertainty(.) %>% filter(coef < 0) %>% select(id, time)

pb <- stand_disp %>%
  filter(mod_name == "Standard Controls w. Temp" & ets_spec== "w. ETS" & ar == 0 & p_val == 0.01) %>% 
  pull(is) %>% first %>% break_uncertainty(.) %>% filter(coef > 0) %>% select(id, time)

plots <- list()
for(count in c("Belgium", "Canada", "Denmark", "Portugal", "UnitedKingdom", "UnitedStates")){
  b <- nb$time[nb$id == count] #%>% as.list
  
  demand_chan <- dem_disp %>%
    arrange(dep) %>% 
    convert_mult %>%
    filter(id == count) %>% 
    plot_country(., country = count, bs = b, na.rm = TRUE)

   source_lev_chan <- lev_disp %>%
     arrange(dep) %>% 
    convert_mult %>%
    filter(id == count) %>%
    plot_country(., country = count, bs = b, na.rm = TRUE)

  source_share_chan <- ov_disp %>%
    arrange(dep) %>% 
    convert_mult %>%
    filter(id == count) %>%
    plot_country(., country = count, bs = b, na.rm = TRUE)
  
  ptemp <- list(grid.arrange(arrangeGrob(demand_chan, top = "Demand Channel"), arrangeGrob(source_lev_chan, top = "Tech Channel: Levels"), arrangeGrob(source_share_chan, top = "Tech Channel: Shares"), ncol = 3, top = count))
  names(ptemp) <- count
  
  plots <- c(plots, ptemp)
}

```


```{r, echo = FALSE, results = 'asis', fig.height = 16}

for(cty in c("Belgium", "Canada", "Denmark", "Portugal", "UnitedKingdom", "UnitedStates")){
  cat('#### ', cty, '   \n')
  cat('\n')
  cat('\n')
  plot.new()
  plots[[cty]] %>% grid.draw
  plot.new()
        cat('\n')
        cat('\n')
}

```


## Positive Emissions Breaks  {.tabset}
*Note:* Countries in which no break was detected are excluded from these overview plots.\

### Emissions {.tabset}

```{r, echo = FALSE, fig.height = 12}

stand_forms <- stand_disp %>%
  filter(mod_name == "Standard Controls w. Temp" & ets_spec== "w. ETS" & ar == 0 & p_val < 0.05) %>% 
  mutate(model = paste("p=",p_val))

stand_forms %>% plot_comp(., sign = "pos")

```

### Channels {.tabset}
```{r, echo = FALSE, include = FALSE}

plots_p <- list()
for(count in c("Australia", "Austria", "France", "Germany", "Japan", "Netherlands", "NewZealand", "Portugal", "Spain", "Sweden", "Switzerland")){
  print(count)
  b <- pb$time[pb$id == count] #%>% as.list

  demand_chan <- dem_disp %>% 
    arrange(dep) %>%
    convert_mult %>%
    filter(id == count) %>%
    plot_country(., country = count, bs = b, na.rm = TRUE)

   source_lev_chan <- lev_disp %>%
     arrange(dep) %>%
    convert_mult %>%
    filter(id == count) %>%
    plot_country(., country = count, bs = b, na.rm = TRUE)

  source_share_chan <- ov_disp %>%
    arrange(dep) %>%
    convert_mult %>%
    filter(id == count) %>%
    plot_country(., country = count, bs = b, na.rm = TRUE)

  ptemp <- list(grid.arrange(arrangeGrob(demand_chan, top = "Demand Channel"), arrangeGrob(source_lev_chan, top = "Tech Channel: Levels"), arrangeGrob(source_share_chan, top = "Tech Channel: Shares"), ncol = 3, top = count))
  names(ptemp) <- count

  plots_p <- c(plots_p, ptemp)
}

```


```{r, echo = FALSE, results = 'asis', fig.height = 16}

for(cty in c("Australia", "Austria", "France", "Germany", "Japan", "Netherlands", "NewZealand", "Portugal", "Spain", "Sweden", "Switzerland")){
  cat('#### ', cty, '   \n')
  cat('\n')
  cat('\n')
  plot.new()
  plots_p[[cty]] %>% grid.draw
  plot.new()
        cat('\n')
        cat('\n')
}

```
