---
title: "Analysis_BRICS"
author: "Ebba Mark"
date: "`r Sys.Date()`"
output: html_document
---

# Load libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())
library(data.table)
library(tidyverse)
library(openxlsx)
library(stringr)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(fastDummies)
library(janitor)
library(plm)

source(here("code/dicts.R"))

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

```

# Create controls, scale emissions (ktco2/ktco2e), other required transformations (FD, lags, growth rates)

Three available GDP indicators: 
- WB GDP current US$ (gdp)   
- OECD 2015 constant prices US$ (gdp_const_oecd)   
- WB 2015 constant price $US (gdp_const) 

NOTE: Canada is missing WB 2015 constant price US$ data points from 1990-1996, 
Canada's WB TS has been replaced with the OECD data
```{r}

dfi <- data %>% 
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2, 
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000,
         log_electricity_generation = log(electricity_generation))

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L), 
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>% 
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))
         
```

# Testing BRICS+
```{r}

brics_plus <- c("Brazil", "Russia", "India", "China", "South Africa", "Indonesia", "Argentina", "Nigeria", "Saudi Arabia", "Turkey", "Egypt", "Iran", "Vietnam", "Thailand", "United Arab Emirates")

# Complete except weather for 1990-2021 (except Iran, UAE in 2021)
# Complete for weather 2000-2021
stan_vars <- c("l_edgar_v7", "lgdp_wb", "lpop", "lgdp_wb_sq", "HDD16dailybypop", "CDD18dailybypop")

# Complete for 2000-2021 except a few 2021 observations
# 1990-2021: Nigeria missing 1990-2000 for all shares
# EXCLUDE NIGERIA in 1990-2021
share_vars <- c("low_carbon_share_elec","renewables_share_elec", "fossil_share_elec", "solar_share_elec", "hydro_share_elec", "wind_share_elec", "nuclear_share_elec", "oil_share_elec", "coal_share_elec", "gas_share_elec")

# Exclude Nigeria 1990-2000
gen_vars <- c("log_electricity_generation", "log_elec_demand_twh", "log_imports_elec_twh", "log_exports_elec_twh")

source_lev_vars <- c("low_carbon_electricity",                 
         "renewables_electricity",                 
         "fossil_electricity",
         "coal_electricity",
         "gas_electricity", 
         "hydro_electricity", 
         "nuclear_electricity",
         "oil_electricity", 
         "solar_electricity", 
         "wind_electricity")

for(s in source_lev_vars){
  print(s)
  df %>% filter(country %in% brics_plus & year >= 1990) %>% select(country, year, s) %>% ungroup %>% 
    filter(!complete.cases(.)) %>% print
}

df %>% filter(country %in% brics_plus & year >= 1990) %>% 
  ggplot(aes(x = year, y = solar_share_elec)) + 
  geom_line() +
  facet_wrap(~country)

```

```{r}
temp <- read.csv(here('data/raw/IEA_elec_data/IEA_EI_CH_natl.csv')) %>% 
  rename(elec_gwh = Value, year = Time) %>%
  mutate(country = ifelse(Country %in% names(getcountry), unname(getcountry[Country]), ifelse(Country == "Republic of Turkiye", "Turkey", Country)),
         elec_twh = elec_gwh/1000) %>%
  select(country, Balance, year, elec_twh) %>%
  pivot_wider(id_cols = c(country, year), names_from = Balance, values_from = elec_twh, names_glue = "{Balance}_{.value}") %>% 
    clean_names %>% 
  mutate(net_imports_twh = imports_elec_twh - exports_elec_twh,
         elec_demand_twh = total_gross_production_elec_twh + net_imports_twh) %>% 
  select(country, year, elec_demand_twh, exports_elec_twh, imports_elec_twh) %>% 
  mutate(log_imports_elec_twh = log(imports_elec_twh + 1), log_exports_elec_twh = log(exports_elec_twh + 1),
         log_elec_demand_twh = log(imports_elec_twh + 1))

ggplot()+
  geom_line(data = filter(temp, country %in% brics_plus & year >= 1990), aes(y = log_exports_elec_twh, x = year)) +
  facet_wrap(~country, scales = "free")

temp %>% filter(country %in% brics_plus & year >= 1990) %>% filter(!complete.cases(.))

dem_df <- df %>% select(country, year, lgdp_wb, lpop, lgdp_wb_sq, log_electricity_generation, HDD16dailybypop, CDD18dailybypop) %>% 
  left_join(., temp, by = c("country", "year")) %>% 
    filter(country %in% brics_plus & year >= 1990) %>% 
    ungroup
    

```


# Formulas
```{r}

# Emissions
emiss_base <-  "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq"
emiss_weather <- "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + HDD16dailybypop + CDD18dailybypop"

# Shares
controls <- c("~ lgdp_wb + lpop + lgdp_wb_sq",
                 "~ lgdp_wb + lpop + lgdp_wb_sq + + HDD16dailybypop + CDD18dailybypop")

share_forms <- c(paste("low_carbon_share_elec", controls),
                 paste("renewables_share_elec", controls),
                 paste("fossil_share_elec", controls),
                 paste("solar_share_elec", controls),
                  paste("hydro_share_elec", controls),
                  paste("wind_share_elec", controls),
                  paste("nuclear_share_elec", controls),
                  paste("oil_share_elec", controls),
                  paste("coal_share_elec", controls),
                  paste("gas_share_elec", controls))

# Demand Channel
dem_forms <- c(paste("log_electricity_generation", controls))
                 paste("log_elec_demand_twh", controls),
                 paste("log_imports_elec_twh", controls),
                 paste("log_exports_elec_twh", controls))


```

# Emissions
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

brics_ems <- foreach(f = c(emiss_base, emiss_weather), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
      if(grepl("HDD", f)){
        dat <- df %>% filter(country %in% brics_plus & year >= 2000)
      }else{dat <- df %>% filter(country %in% brics_plus & year >= 1990)}
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "BRICS_Plus",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0)
    }

saveRDS(brics_ems, here("output/brics_emissions_models.RDS"))

```

# Demand Channel
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

brics_dem <- foreach(f = c(gen_vars), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
      dat <- dem_df %>% 
        filter(country %in% brics_plus & year >= 1990) %>% 
        group_by(country) %>% 
        mutate(thresh = sum(get(f) != 0, na.rm = TRUE)) %>% 
        filter(thresh >= 8)
      is <- isatpanel(
            data = dat,
            formula = as.formula(paste(f, "~ lgdp_wb + lpop + lgdp_wb_sq")),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = paste(f, "~ lgdp_wb + lpop + lgdp_wb_sq"),
                          country_sample = "BRICS_Plus",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0)
    }

saveRDS(brics_dem, here("output/brics_dem_models.RDS"))


```

# Tech Channel: Shares
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

brics_shares <- foreach(f = c(share_vars[share_vars != "solar_share_elec"]), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
      dat <- df %>% 
        filter(country %in% brics_plus[brics_plus != "Nigeria"] & year >= 1990) %>% 
        group_by(country) %>% 
        mutate(thresh = sum(get(f) != 0, na.rm = TRUE)) %>% 
        filter(thresh >= 30)
      is <- isatpanel(
            data = dat,
            formula = as.formula(paste(f, "~ lgdp_wb + lpop + lgdp_wb_sq")),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = paste(f, "~ lgdp_wb + lpop + lgdp_wb_sq"),
                          country_sample = "BRICS_Plus",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0)
    }

saveRDS(brics_shares, here("output/brics_source_shares_models.RDS"))

# for(test in share_vars){
#   print(test) 
#   df %>% 
#         filter(country %in% brics_plus[brics_plus != "Nigeria"] & year >= 1990) %>% 
#         group_by(country) %>% 
#         mutate(thresh = sum(get(test) != 0, na.rm = TRUE)) %>% 
#         filter(thresh >= 30) %>% print}

```
