---
title: "Full_Analysis"
author: "Ebba Mark"
date: "`r Sys.Date()`"
output: html_document
---

# Load libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())
library(data.table)
library(tidyverse)
library(openxlsx)
library(stringr)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(fastDummies)
library(janitor)
library(plm)
# 
# install.packages(
#   "https://github.com/gsucarrat/gets/raw/master/gets_devel.tar.gz",
#   repos = NULL, type = "source"
# )

#devtools::install_github("moritzpschwarz/getspanel")

source(here("code/dicts.R"))

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

```

# Create controls, scale emissions (ktco2/ktco2e), other required transformations (FD, lags, growth rates)

Three available GDP indicators: 
- WB GDP current US$ (gdp)   
- OECD 2015 constant prices US$ (gdp_const_oecd)   
- WB 2015 constant price $US (gdp_const) 

NOTE: Canada is missing WB 2015 constant price US$ data points from 1990-1996, 
Canada's WB TS has been replaced with the OECD data
```{r}

dfi <- data %>% 
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2, 
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L), 
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>% 
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))
         
```

# Shares

## Data check
Share of electricity generation per fuel type
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review

```{r} 

shares_df <- 
  df %>%
  mutate(fossil_share_elec = ifelse(is.na(fossil_share_elec), 100 - low_carbon_share_elec, fossil_share_elec)) %>%
  filter(country %in% sel[sel != "Luxembourg"] & year >=1990) %>% 
  select(country, year, ets_price,
        l_edgar_v7,
        lgdp_wb, lgdp_wb_sq, lpop, EU_ETS_05, EU_ETS_08, EU_ETS_13, hdd, cdd,
        low_carbon_share_elec,
        renewables_share_elec,
        #other_renewables_share_elec,
        #other_renewables_share_elec_exc_biofuel,
        biofuel_share_elec,
        fossil_share_elec,
          coal_share_elec,
          oil_share_elec,
          gas_share_elec,
          nuclear_share_elec,
          solar_share_elec,
          wind_share_elec,
          hydro_share_elec,
         #contains("_electricity"),
         #-per_capita_electricity
         )


```

## Formulas
```{r}

controls <- c("~ lgdp_wb + lpop + lgdp_wb_sq",
                 "~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd",
                 "~ lpop + hdd + cdd")

share_forms <- c(paste("low_carbon_share_elec", controls),
                 paste("renewables_share_elec", controls),
                 paste("fossil_share_elec", controls),
                 paste("solar_share_elec", controls),
                  paste("hydro_share_elec", controls),
                  paste("wind_share_elec", controls),
                  paste("nuclear_share_elec", controls),
                  paste("oil_share_elec", controls),
                  paste("coal_share_elec", controls),
                  paste("gas_share_elec", controls))

ets_covs <- c("+ EU_ETS_05 + EU_ETS_08 + EU_ETS_13")

shares_ets <- paste(rep(share_forms, each = length(ets_covs)), ets_covs)


```

## Code: Standard
Share of electricity generation per fuel type
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review

```{r} 

cl <- makeCluster(6)
registerDoParallel(cl)

shares_sources <- foreach(f = c(share_forms), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- shares_df %>%
    filter(country %in% sel[sel != "Luxembourg"] & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

saveRDS(shares_sources, here("output/temp/shares_bysource_ar_nolux.RDS"))
#saveRDS(shares_sources_nolux, here("output/temp/shares_bysource_noar_nolux.RDS"))
#saveRDS(shares_sources, here("output/temp/shares_bysource_noar.RDS"))

```

## Code: ETS
```{r}

cl <- makeCluster(7)
registerDoParallel(cl)

temp_ets_prices <- foreach(f = c(shares_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
   #foreach(b = c(10, 20, 30), .combine = rbind) %:%
     foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
     dat <- df %>%
     filter(country %in% sel[sel != "Luxembourg"] & year >= 1990) %>% 
       mutate(ets_price = ifelse(year < 2005, 0, ets_price))
       is <- isatpanel(
            data = dat,
             formula = as.formula(f),
             index = c("country", "year"),
             effect = "twoways",
             iis = TRUE,
             fesis = TRUE,
             ar = a,
             t.pval = p.value,
             max.block.size = 20
             )
           temp_ets_prices = tibble(source = f,
                           country_sample = "NOLUX_EU15+selected",
                           year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                           is = list(is),
                           iis = TRUE,
                           b_size = 20,
                          ar = a)
     }

saveRDS(temp_ets_prices, here("output/temp/mod_ets_price.RDS"))

#saveRDS(shares_ets, here("output/temp/shares_ets_noar.RDS"))
saveRDS(temporary_ets_shares, here("output/temp/temporary_ets_shares.RDS"))

```


## Code: Standard (NUCLEAR)
Share of electricity generation per fuel type
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review

```{r} 

cl <- makeCluster(6)
registerDoParallel(cl)

nuclear_shares <- c("nuclear_share_elec ~ lgdp_wb + lpop + lgdp_wb_sq",
                    "nuclear_share_elec ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd",
                    "nuclear_share_elec ~ lpop + hdd + cdd",
                    "nuclear_share_elec ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13",
                    "nuclear_share_elec ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13", 
                    "nuclear_share_elec ~ lpop + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13")             

share_nuclear <- foreach(f = c(nuclear_shares), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- shares_df %>%
    filter(country %in% sel[!(sel %in% c("Australia", "Austria", "Denmark", "Greece", "Ireland", "Italy", "Portugal", "New Zealand", "Luxembourg"))] & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "EU_No_Zeros",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

saveRDS(share_nuclear, here("output/temp/shares_nuclear_no_zeros.RDS"))

```


############################################################################################################################################
# Logit-transformed Shares
## Data
```{r}

logit_shares <- shares_df_simple %>%
  mutate(fossil_share_elec = ifelse(is.na(fossil_share_elec), 100 - low_carbon_share_elec, fossil_share_elec)) %>%
  filter(country %in% sel[sel!= "Luxembourg"] & year >=1990) %>% 
  select(country, year, ets_price,
       # l_edgar_v7,
        lgdp_wb, lgdp_wb_sq, lpop, EU_ETS_05, EU_ETS_08, EU_ETS_13, hdd, cdd,
        low_carbon_share_elec,
        renewables_share_elec,
        # other_renewables_share_elec,
        # other_renewables_share_elec_exc_biofuel,
        #biofuel_share_elec,
        fossil_share_elec,
        coal_share_elec,
        oil_share_elec,
        gas_share_elec,
        nuclear_share_elec,
        solar_share_elec,
        wind_share_elec,
        hydro_share_elec,
         ) %>% ungroup %>% 
  mutate(across(low_carbon_share_elec:hydro_share_elec, ~.x/100)) %>% 
  mutate(across(low_carbon_share_elec:hydro_share_elec, ~log(.x/(1-.x)), .names = "logit_{.col}"))


# prop_logit <- log(prop/(1-prop))
# prop_fit <- exp(fit_logit)/(1+exp(fit_logit))
#   mutate(across(logit_low_carbon_share_elec:logit_fossil_share_elec, ~exp(.x)/(1+ exp(.x)), .names = "test_{.col}"))

```

## Formulas
```{r}

logit_forms <- paste0("logit_", share_forms)

logit_ets <- paste(rep(logit_forms, each = length(ets_covs)), ets_covs)

```

## Code: Standard
```{r} 

cl <- makeCluster(6)
registerDoParallel(cl)

logit_mods <- foreach(f = logit_forms[!grepl("coal", logit_forms) & !grepl("nuclear", logit_forms)], .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
      dat <- logit_shares
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

```

## Code: ETS
```{r}
cl <- makeCluster(6)
registerDoParallel(cl)

# 72 models
logit_mods_ets <- foreach(f = c(logit_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
      dat <- logit_shares
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

```

## Code: Nuclear & Coal
```{r}

logit_brief_coal <- c(logit_forms, logit_ets)[grepl("coal", c(logit_forms, logit_ets))]
logit_brief_nuclear <- c(logit_forms, logit_ets)[grepl("nuclear", c(logit_forms, logit_ets))]
    
cl <- makeCluster(6)
registerDoParallel(cl)


coal_logit <- foreach(f = c(logit_brief_coal), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
 # foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01), .combine = rbind) %dopar% {
    dat <- logit_shares %>% filter(country != "Switzerland")
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = 0,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "EU_No_Zeros",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0)
    }

nuclear_logit <- foreach(f = c(logit_brief_nuclear), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
    dat <- logit_shares %>% 
      filter(country %in% sel[!(sel %in% c("Australia", "Austria", "Denmark", "Greece", "Ireland", "Italy", "Portugal", "New Zealand", "Luxembourg"))] & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "EU_No_Zeros",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

logit_mods_ets %>% 
  rbind(logit_mods) %>% 
  filter(!grepl("coal", source) & !grepl("nuclear", source)) %>% 
  rbind(coal_logit) %>% 
  rbind(nuclear_logit)
#saveRDS(here("output/temp/logit_transformed_shares_ff_ren_lc.RDS"))

```

# Levels (log)
Unit: Electricity generation per source (TWH)
Additional option: Electricity generation per fuel type, measured in terawatt-hours
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review

Difference between electricity generation and consumption here...ex. exported wind power 

WARNING: replaced Switzerland and New Zealand's OWID data with IEA data - not consistent perhaps. Consider using ONLY IEA data (requires more investigation of inconsistencies between the two datasets and the IEA's categorization of coal, oil, and gas data: https://stats2.digitalresources.jisc.ac.uk/metadata/IEA/Elec/Electricity_Information_Documentation_2022Edition.pdf)
```{r}

gen <- df %>% 
  filter(country %in% sel[sel != "Luxembourg"] & year >=1990) %>% 
  select(country, year, ets_price,
        # l_edgar_v7,
         lgdp_wb, lgdp_wb_sq, lpop, EU_ETS_05, EU_ETS_08, EU_ETS_13, hdd, cdd,
         electricity_generation,
         low_carbon_electricity,                 
         renewables_electricity,                 
         fossil_electricity,
         coal_electricity,
         gas_electricity, 
         hydro_electricity, 
         nuclear_electricity,
         oil_electricity, 
         solar_electricity, 
         wind_electricity) %>% 
  rename(fossil_electricity_raw = fossil_electricity)
  
iea_elec <- readRDS(here("data/out/IEA_elec_data_by_source.RDS"))

gen$coal_electricity[gen$country == "New Zealand"] <- iea_elec$sum_value[iea_elec$country == "New Zealand" & iea_elec$code == "coal"]
gen$oil_electricity[gen$country == "New Zealand"] <- iea_elec$sum_value[iea_elec$country == "New Zealand" & iea_elec$code == "oil"]
gen$gas_electricity[gen$country == "New Zealand"] <- iea_elec$sum_value[iea_elec$country == "New Zealand" & iea_elec$code == "gas"]

gen$coal_electricity[gen$country == "Switzerland"] <- iea_elec$sum_value[iea_elec$country == "Switzerland" & iea_elec$code == "coal"]
gen$oil_electricity[gen$country == "Switzerland"] <- iea_elec$sum_value[iea_elec$country == "Switzerland" & iea_elec$code == "oil"]
gen$gas_electricity[gen$country == "Switzerland"] <- iea_elec$sum_value[iea_elec$country == "Switzerland" & iea_elec$code == "gas"]

gen_df <- gen %>% 
  mutate(fossil_electricity = coal_electricity + oil_electricity + gas_electricity) %>% 
  mutate(across(electricity_generation:fossil_electricity, ~log(.x + 1), .names = "log_{.col}"))

gen_df %>% 
  select(country, year, contains("log")) %>%
  pivot_longer(!c(country, year), names_to = "indic", values_to = "log_val") %>% 
  ggplot(aes(x = year, y = log_val, color = indic)) +
           geom_line() +
    facet_wrap(~country, scales = "free")

gen_df %>% select(year, country, contains("log"), -log_fossil_electricity_raw) %>% ungroup %>% filter(!complete.cases(.))


gen_df %>% select(country, year, electricity_generation, coal_electricity, oil_electricity, gas_electricity) %>% filter(country %in% c("Switzerland", "New Zealand")) %>% 
  mutate(coal_share_elec = (coal_electricity/electricity_generation)*100,
         oil_share_elec = (oil_electricity/electricity_generation)*100,
         gas_share_elec = (gas_electricity/electricity_generation)*100)

```

## Formulas
```{r}

source_lev_forms <-share_forms <- c(paste("log_low_carbon_electricity", controls),
                 paste("log_renewables_electricity", controls),
                 paste("log_fossil_electricity", controls),
                 paste("log_solar_electricity", controls),
                  paste("log_hydro_electricity", controls),
                  paste("log_wind_electricity", controls),
                  paste("log_nuclear_electricity", controls),
                  paste("log_oil_electricity", controls),
                  paste("log_coal_electricity", controls),
                  paste("log_gas_electricity", controls))

source_lev_ets <- paste(rep(source_lev_forms, each = length(ets_covs)), ets_covs)


```

## Code: Standard
```{r} 

cl <- makeCluster(6)
registerDoParallel(cl)

# 60 models?
source_lev_mods <- foreach(f = c(source_lev_forms), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01), .combine = rbind) %dopar% {
      dat <- gen_df
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }


```

## Code: ETS
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

# 120 models?
source_lev_ets_mods <- foreach(f = c(source_lev_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.01), .combine = rbind) %dopar% {
      dat <- gen_df
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

source_lev_mods %>% 
  rbind(source_lev_ets_mods) %>% 
saveRDS(here("output/temp/gen_by_source_mods.RDS"))

```

## Code: Nuclear and Coal
```{r}

source_lev_coal <- c(source_lev_forms, source_lev_ets)[grepl("coal", c(source_lev_forms, source_lev_ets))]
source_lev_nuclear <- c(source_lev_forms, source_lev_ets)[grepl("nuclear", c(source_lev_forms, source_lev_ets))]

cl <- makeCluster(6)
registerDoParallel(cl)

coal_source <- foreach(f = c(source_lev_coal), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
    dat <- gen_df %>% filter(country != "Switzerland")
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "EU_No_Zeros",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

nuclear_source <- foreach(f = c(source_lev_nuclear), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
    dat <- gen_df %>% 
      filter(country %in% sel[!(sel %in% c("Australia", "Austria", "Denmark", "Greece", "Ireland", "Italy", "Portugal", "New Zealand", "Luxembourg"))] & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "EU_No_Zeros",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }
    
source_lev_mods %>%
  rbind(source_lev_ets_mods) %>% 
  filter(!grepl("coal", source) & !grepl("nuclear", source)) %>% 
  rbind(coal_source, nuclear_source) %>% saveRDS(here("output/temp/gen_by_source_mods.RDS"))

```


# Consumption/Production
```{r}

iea_supp <- readRDS(here("data/temp/iea_elec_data.RDS")) %>% 
  filter(country != "Luxembourg") %>%
  mutate(across(!c(country, year), log, .names = "{'log'}_{.col}" )) %>% 
  select(country, year, log_elec_demand_twh)

cons_df <- df %>%
  filter(country %in% sel[sel != "Luxembourg"] & year >=1990) %>% 
  select(country, year, 
         ets_price,
         l_edgar_v7,
         lgdp_wb, lgdp_wb_sq, lpop, EU_ETS_05, EU_ETS_08, EU_ETS_13, 
         hdd, cdd,
         electricity_generation) %>% 
  mutate(log_electricity_generation = log(electricity_generation)) %>% ungroup %>% 
  left_join(., iea_supp, by = c('country', 'year'))

cons_df %>% 
  filter(country %in% sel[sel != "Luxembourg"] & year >= 1990) %>% 
  select(country, year, lgdp_wb, lgdp_wb_sq, lpop, hdd, cdd, log_electricity_generation, log_elec_demand_twh) %>% 
  filter(!complete.cases(.))

```

## Formulas
```{r}

prod_forms <- c(paste("log_electricity_generation", share_controls),
                 paste("log_elec_demand_twh", share_controls))

prod_ets <- paste(rep(prod_forms, each = length(ets_covs)), ets_covs)

```


## Code

```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

prod_mods <- foreach(f = c(prod_forms, prod_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- cons_df %>%
    filter(country %in% sel[sel != "Luxembourg"] & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          prod_mods = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

saveRDS(prod_mods, here("output/temp/production_data_models.RDS"))


prod_mods <- readRDS(here("output/temp/production_data_models.RDS"))

```


# Imports/Exports
```{r}

iea_imp <- readRDS(here("data/temp/iea_elec_data.RDS")) %>% 
  filter(country != "Luxembourg") %>%
  select(country, year, exports_elec_twh, imports_elec_twh) %>% 
  mutate(log_imports_elec_twh = log(imports_elec_twh + 1), log_exports_elec_twh = log(exports_elec_twh + 1))

cons_df <- df %>%
  filter(country %in% sel[sel != "Luxembourg"] & year >=1990) %>% 
  select(country, year, 
         ets_price,
         l_edgar_v7,
         lgdp_wb, lgdp_wb_sq, lpop, EU_ETS_05, EU_ETS_08, EU_ETS_13, 
         hdd, cdd) %>% 
  ungroup %>% 
  left_join(., iea_imp, by = c('country', 'year'))

cons_df %>% 
  filter(country %in% sel[sel != "Luxembourg"] & year >= 1990) %>% 
  select(country, year, lgdp_wb, lgdp_wb_sq, lpop, hdd, cdd, log_imports_elec_twh, log_exports_elec_twh) %>% 
  filter(!complete.cases(.))

cons_df %>% 
  ggplot(aes(x = year)) +
  geom_line(aes(y = log_imports_elec_twh)) +
  geom_line(aes(y = log_exports_elec_twh)) +
  facet_wrap(~country, scales = "free")

```

## Formulas
```{r}

ports_forms <- c(paste("log_imports_elec_twh", controls),
                 paste("log_exports_elec_twh", controls))

ports_ets <- paste(rep(ports_forms, each = length(ets_covs)), ets_covs)

```


## Code

```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

ports_mods <- foreach(f = c(ports_forms, ports_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.01), .combine = rbind) %dopar% {
    dat <- cons_df %>%
    filter(country %in% sel[!(sel %in% c("Luxembourg", "Australia", "Japan", "New Zealand"))] & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          prod_mods = tibble(source = f,
                          country_sample = "EU_No_Zeros",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

saveRDS(ports_mods, here("output/temp/imports_export_models.RDS"))

```

# Supplemental Shares (NZ & Switzerland corrected)
Additional option: Electricity generation per fuel type, measured in terawatt-hours
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review
```{r}

shares_df_simple <- shares_df
gen_simple <- gen_df %>% select(country, year, electricity_generation, coal_electricity, oil_electricity, gas_electricity) %>% filter(country %in% c("Switzerland", "New Zealand")) %>% 
  mutate(coal_share_elec = (coal_electricity/electricity_generation)*100,
         oil_share_elec = (oil_electricity/electricity_generation)*100,
         gas_share_elec = (gas_electricity/electricity_generation)*100)

shares_df_simple$coal_share_elec[shares_df_simple$country == "New Zealand"] <- gen_simple$coal_share_elec[gen_simple$country == "New Zealand"]
shares_df_simple$oil_share_elec[shares_df_simple$country == "New Zealand"] <- gen_simple$oil_share_elec[gen_simple$country == "New Zealand"]
shares_df_simple$gas_share_elec[shares_df_simple$country == "New Zealand"] <- gen_simple$gas_share_elec[gen_simple$country == "New Zealand"]

shares_df_simple$coal_share_elec[shares_df_simple$country == "Switzerland"] <- gen_simple$coal_share_elec[gen_simple$country == "Switzerland"]
shares_df_simple$oil_share_elec[shares_df_simple$country == "Switzerland"] <- gen_simple$oil_share_elec[gen_simple$country == "Switzerland"]
shares_df_simple$gas_share_elec[shares_df_simple$country == "Switzerland"] <- gen_simple$gas_share_elec[gen_simple$country == "Switzerland"]


```

## Formulas
```{r}

share_brief_forms <- c(paste("fossil_share_elec", controls),
                  paste("oil_share_elec", controls),
                  paste("coal_share_elec", controls),
                  paste("gas_share_elec", controls))

share_brief_ets <- paste(rep(share_brief_forms, each = length(ets_covs)), ets_covs)

```

## Code: Standard
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

# 24 models
supp_shares <- foreach(f = c(share_brief_forms), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01), .combine = rbind) %dopar% {
    dat <- shares_df_simple
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

```

## Code: ETS
```{r}
cl <- makeCluster(6)
registerDoParallel(cl)

supp_shares_ets <- foreach(f = c(share_brief_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01), .combine = rbind) %dopar% {
    dat <- shares_df_simple
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }
```

## Code: Coal
```{r}

share_brief_coal <- c(share_brief_forms, share_brief_ets)[grepl("coal", c(share_brief_forms, share_brief_ets))]

cl <- makeCluster(6)
registerDoParallel(cl)

# 24 models
coal_shares <- foreach(f = c(share_brief_coal), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
    dat <- shares_df_simple %>% filter(country != "Switzerland")
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "EU_No_Zeros",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

supp_shares %>% 
  rbind(supp_shares_ets) %>% 
  filter(!grepl("coal", source)) %>% 
  rbind(coal_shares) %>% 
saveRDS(here("output/temp/supp_share_elec_oil_coal_gas.RDS"))

```
