---
title: "Analysis"
author: "Ebba Mark"
date: "`r Sys.Date()`"
output: html_document
---

# Load libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())
library(data.table)
library(tidyverse)
library(openxlsx)
library(stringr)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(fastDummies)
# 
# install.packages(
#   "https://github.com/gsucarrat/gets/raw/master/gets_devel.tar.gz",
#   repos = NULL, type = "source"
# )

# devtools::install_github("moritzpschwarz/getspanel")

source(here("code/dicts.R"))

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

```

# Create controls, scale emissions (ktco2/ktco2e), other required transformations (FD, lags, growth rates)

```{r}

data <- data %>% 
  mutate(gdp_sq = gdp^2,
          lpop = log(pop),
          lgdp = log(gdp),
          lgdp_sq = log(gdp)^2,
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

data <- data %>% group_by(country) %>%
  # Lags (3), first-difference, growth rate of log emissions (EDGAR V7), lgdp, lpop, lgdp_sq
  mutate(across(c(l_edgar_v7, lgdp, lpop, lgdp_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L), 
         d = ~c(NA, diff(.x, differences = 1)),
         g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>% 
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))
         
```

## Test runs {.tabset}
# Reproducible loop testing EDGAR V7.0
dependent variable: edgar_v7_elec_ktco2

```{r, eval = FALSE}
tot <- unique(c(EU31, OECD))
dat <- data %>% 
  filter(country %in% tot & year >= 2000) %>%
  select(country, year, edgar_v7_elec_ktco2, lgdp, lpop, lgdp_sq) %>% as.data.frame()


ltitle="output/Results_CO2Drivers_Analysis_test.txt"

for(p.value in c(.05, .01, .001)){
    
    is <- isatpanel(
      data = dat,
      formula = edgar_v7_elec_ktco2 ~ lgdp + lgdp_sq + lpop,
      index = c("country", "year"),
      effect = "twoways",
      iis = TRUE,
      fesis = TRUE,
      t.pval=p.value
)
    
    # Print analysis results
    cat(
      paste0(
        " \n ###########################", 
        " \n # p-value: ", p.value,
        " \n \n "), 
      file = ltitle, 
      append = TRUE)
    
    sink(ltitle, append=TRUE)
    print(is)
    sink()
    
    cat(" \n \n \n \n \n", 
        file = ltitle, 
        append = TRUE)
  }



```

# Simple loop

```{r}

run_simple <- function(fs, country_sample, yr_min, p.value){
    dat <- data %>% 
    filter(country %in% country_sample & year >= yr_min)  %>% as.data.frame()
        is <- isatpanel(
            data = dat,
            formula = as.formula(fs),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = 20,
            )
        return(is) }

# Example
test <- run_simple(EU15, 1990, 0.001, )
#saveRDS(test, here('output/test.RDS'))

#test <- readRDS(here('output/test.RDS'))

```

# Parallel
96 base models
Saved as "output/edgar_v7_models.RDS"

```{r}
# Vector of different emissions data sources
dep_vars = c('l_edgar_v7', 
             'edgar_v7_elec_ktco2',
             'owid_1_elec_heat_ktco2e',
             'owid_2_elec_ktco2e',
             'bp_energy_ktco2',
             'iea_elec_heat_ktco2',
             'oecd_ktco2e')

# Vector of country samples (EU, OECD, OECD+, BRICS, Other)
groups <- list('all' = unique(data$country),
               'EU15' = EU15,
               'EU31' = EU31,
               'OECD' = OECD,
               #'OECD_plus' = c(OECD, )
               'BRICS' = c("Brazil", "Russia", "India", "China", "South Africa"),
               'Other' = c("Nigeria", "Bangladesh", "Indonesia", "Vietnam", "Thailand", "Egypt", "Saudi Arabia", "United Arab Emirates")
               #'BRICS_plus' = c(BRICS, ),
               #'Africa_min' = ,
               #'South_America_min' = ,
)

yr_mins <- c(1990, 2000)
```


```{r, eval = FALSE}

cl <- makeCluster(6)
registerDoParallel(cl)

tot_models <- foreach (k = 2:5, .combine=rbind, .packages = c('tidyverse', 'getspanel')) %:%
    foreach(y = yr_mins, .combine = rbind) %:%
    foreach(i = c(TRUE, FALSE), .combine = rbind) %:%
    foreach(b = c(20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- data %>% 
    filter(country %in% groups[[k]] & year >= y) %>%
    select(country, year, dep_vars[1], lgdp, lpop, lgdp_sq) %>% as.data.frame()
      is <- isatpanel(
            data = dat,
            formula = as.formula(paste0(dep_vars[[1]], "~ lgdp + lpop + lgdp_sq")),
            index = c("country", "year"),
            effect = "twoways",
            iis = i,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = b
            )
          models = tibble(source = dep_vars[1], 
                                       country_sample = names(groups[k]), 
                                       year_range = paste0(min(dat$year),":",max(dat$year)), 
                                       p_val = p.value, 
                                       is = list(is),
                          iis = i,
                          b_size = b)
    }

#saveRDS(models, here("output/edgar_v7_models_all.RDS"))

```

# Extracting results and plots for one specification

```{r}

models <- readRDS(here("output/edgar_v7_models_all.RDS"))

# functioning plot extractor
# get_model <- function(country_sample, year_range, p.val, l_iis, b_size){
#   mod <- models$is[models$country_sample == country_sample & 
#                      models$year_range == year_range & 
#                      models$p_val == p.val & 
#                      models$iis == l_iis & 
#                      models$b_size == b_size]
#   p <- mod %>% lapply(function(x) plot(x, zero_line = FALSE))
#   p_grid <- mod %>% lapply(plot_grid)
#   return(list(results = mod, plot = p, plot_grid = p_grid))
# }

get_model <- function(ct_sample, yr_range, p.val, l_iis, b_sz){
 m <- models %>% filter(country_sample == ct_sample & 
                     year_range == yr_range & 
                     p_val == p.val & 
                     iis == l_iis & 
                     b_size == b_sz)
  mod <- m %>% pull(is) %>% first()
  p <- mod %>% plot(zero_line = FALSE)
  p_grid <- mod %>% plot_grid
  mt <- m$main_title
  st <- m$sub_title
  return(list(results = mod, plot = p, plot_grid = p_grid, main_title = mt, sub_title = st))
}

# Examples:
te <- get_model('EU15', "1990:2021", 0.001, TRUE, 20)
te$main_title
te$plot
te$plot_grid
te$sub_title

```

# Identified country group
EU-15, US, Canada, NZ, Australia, Japan, Switzerland

# AR version of original model specifications (only varying iis, p-value, block size, time horizon)
```{r}

# "sel" to be moved to dicts
sel <- c(EU15, "United States", "Canada", "New Zealand", "Australia", "Japan", "Switzerland")

cl <- makeCluster(4)
registerDoParallel(cl)

ar_models <- foreach(y = yr_mins, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
    foreach(i = c(TRUE, FALSE), .combine = rbind) %:%
    foreach(b = c(20, 30), .combine = rbind) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- data %>% 
    filter(country %in% sel & year >= y) %>%
    select(country, year, dep_vars[1], lgdp, lpop, lgdp_sq) %>% as.data.frame()
      is <- isatpanel(
            data = dat,
            formula = as.formula(paste0(dep_vars[[1]], "~ lgdp + lpop + lgdp_sq")),
            ar = a,
            index = c("country", "year"),
            effect = "twoways",
            iis = i,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = b
            )
          models = tibble(source = dep_vars[1], 
                                       country_sample = "EU15+selected", 
                                       year_range = paste0(min(dat$year),":",max(dat$year)), 
                                       p_val = p.value, 
                                       is = list(is),
                          iis = i,
                          b_size = b,
                          ar = a)
    }

tot_models <- ar_models %>% mutate(main_title = paste0(country_sample, ": ", substr(year_range,1,4),"-", substr(year_range,6,9)), sub_title = paste0("Specifications: p.value = ",p_val, "; iis = ", iis, "; block size = ", b_size))

#saveRDS(tot_models, "output/edgar_v7_EU15_plus.RDS")
#saveRDS(ar_models, "output/edgar_v7_EU15_plus_AR.RDS")

# gen_plots('EU15+selected', "2000:2021")
# 
# for (i in 1:24){
#   ar_models %>% 
#     slice(i) %>% 
#     pull(is) %>% 
#     first() %>% 
#     plot(title = paste(ar_models$country_sample[i], ar_models$year_range[i], "Specifications: p.value = ",ar_models$p_val[i], "; iis = ", ar_models$iis[i], "; block size = ", ar_models$b_size[i])) %>% print
# }


```

# Testing functional forms
Test on identified country group with:
1% and .1% p-values
iis = TRUE
block size = 20


```{r}
form <- c(
# Standard
"l_edgar_v7 ~ lgdp + lpop + lgdp_sq",

# AR : DONE PREVIOUS CHUNK

# Integrating temperature controls
"l_edgar_v7 ~ lgdp + lpop + lgdp_sq + HDD16dailybypop + CDD18dailybypop",

# Controlling only for population and temperature (removing GDP)
"l_edgar_v7 ~ lpop + HDD16dailybypop + CDD18dailybypop",

# First-differences
"d.l_edgar_v7 ~ d.lgdp + d.lpop + d.lgdp_sq",

# Growth-rates
"g.l_edgar_v7 ~ g.lgdp + g.lpop + g.lgdp_sq")

cl <- makeCluster(6)
registerDoParallel(cl)

for_models <- foreach(f = form[-1], .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
    dat <- data %>% 
    filter(country %in% sel & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f, 
                                       country_sample = "EU15+selected", 
                                       year_range = paste0(min(dat$year),":",max(dat$year)), 
                                       p_val = p.value, 
                                       is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }

saveRDS(for_models, here("output/edgar_v7_EU15_plus_formulas.RDS"))

for(i in 1:16){
  mt <- paste0(for_models$country_sample[i], " (", for_models$year_range[i],")")
  st <- paste0("Formula: ", for_models$source[i])
  pl <- for_models %>% 
    slice(i) %>% 
    pull(is) %>% 
    first() %>% 
    plot(zero_line = FALSE)
  
   print(pl +
    ggtitle(label = mt, subtitle = st))
  
}


```


```{r}

# EU ETS dummies: 2008 and 2013 (2005 available but excluded)
form_ets <- c(paste(form, "+ EU_ETS_08"), paste(form, " + EU_ETS_13"), paste(form, "+ EU_ETS_08 + EU_ETS_13"))
              
cl <- makeCluster(6)
registerDoParallel(cl)

ets_models <- foreach(f = form_ets, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
    foreach(p.value = c(0.01, 0.001), .combine = rbind) %dopar% {
    dat <- data %>% 
    filter(country %in% sel & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f, 
                                       country_sample = "EU15+selected", 
                                       year_range = paste0(min(dat$year),":",max(dat$year)), 
                                       p_val = p.value, 
                                       is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }


saveRDS(ets_models, here("output/models_ets_trials.RDS"))

```

# Common Correlated Effects CCE
```{r}
##### Manually Implementing CCE Estimator
####create x-sectional averages
dat_simple <- data %>% filter(country %in% sel & year >= 1990) %>% select(country, year, l_edgar_v7, lgdp, lpop, lgdp_sq) %>% 
  group_by(year) %>% mutate(mean_l_emissions = mean(l_edgar_v7),
                            mean_lgdp = mean(lgdp),
                            mean_lpop = mean(lpop),
                            mean_lgdp_sq = mean(lgdp_sq)) %>% arrange(country)

# ### generate matrix of interactions so that each unit can have different coefficients
# Below to be automated
i_mean_lemissions <- as.matrix(dat_simple$mean_l_emissions*dummy_cols(dat_simple$country, remove_selected_columns = TRUE))
colnames(i_mean_lemissions) = paste("i_mean_lemissions", colnames(i_mean_lemissions))

i_mean_lgdp <- as.matrix(dat_simple$mean_lgdp*dummy_cols(dat_simple$country, remove_selected_columns = TRUE))
colnames(i_mean_lgdp) = paste("i_mean_lgdp", colnames(i_mean_lgdp))

i_mean_lpop <- as.matrix(dat_simple$mean_lpop*dummy_cols(dat_simple$country, remove_selected_columns = TRUE))
colnames(i_mean_lpop) = paste("i_mean_lpop", colnames(i_mean_lpop))

i_mean_lgdp_sq <- as.matrix(dat_simple$mean_lgdp_sq*dummy_cols(dat_simple$country, remove_selected_columns = TRUE))
colnames(i_mean_lgdp_sq) = paste("i_mean_lgdp_sq", colnames(i_mean_lgdp_sq))

test_simple <- dat_simple %>% cbind(i_mean_lemissions, i_mean_lgdp, i_mean_lpop, i_mean_lgdp_sq) %>% clean_names

m1 <- plm(as.formula(paste("l_edgar_v7 ~ + lgdp + lpop + lgdp_sq + ", paste(names(test_simple[11:94]), collapse = "+"))) , data = test_simple, model="within", effect="twoways", index=c("country", "year"))
summary(m1)

m2 <- plm(l_edgar_v7 ~ + lgdp + lpop + lgdp_sq + i_mean_lemissions + i_mean_lgdp + i_mean_lpop + i_mean_lgdp_sq, data = dat_simple, model="within", effect="twoways", index=c("country", "year"))
summary(m2)

m_pcce <- pcce(l_edgar_v7 ~ + lgdp + lpop + lgdp_sq, data = dat_simple, model="p", index=c("country", "year"))
summary(m_pcce)

#################################################################################

t_pcce5 <- isatpanel(
            data = test_simple,
            formula = as.formula(paste("l_edgar_v7 ~ + lgdp + lpop + lgdp_sq + ", paste(names(test_simple[11:94]), collapse = "+"))),
            index = c("country", "year"),
            effect = "twoways",
            iis = FALSE,
            fesis = FALSE,
            csis = FALSE,
            sis = TRUE,
            t.pval = 0.00000000001,
            max.block.size = 2
            )

# Wondering about user.estimator argument in isatpanel?
# calling plm engine automatically calls plm - any way to modify to call another function in plm package? ie. pcce

saveRDS(t_pcce, here("output/pcce_trial.RDS"))
test <- readRDS(here("output/pcce_trial.RDS"))
```

