---
title: "Full_Analysis"
author: "Ebba Mark"
date: "`r Sys.Date()`"
output: html_document
---

# Load libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())
library(data.table)
library(tidyverse)
library(openxlsx)
library(stringr)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(fastDummies)
library(janitor)
library(plm)
# 
# install.packages(
#   "https://github.com/gsucarrat/gets/raw/master/gets_devel.tar.gz",
#   repos = NULL, type = "source"
# )

# devtools::install_github("moritzpschwarz/getspanel")

source(here("code/dicts.R"))

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

```

# Create controls, scale emissions (ktco2/ktco2e), other required transformations (FD, lags, growth rates)
# 28/10: GDP (current US$) replaced with GDP (constant 2015 $US)

Three available GDP indicators: 
- WB GDP current US$ (gdp)   
- OECD 2015 constant prices US$ (gdp_const_oecd)   
- WB 2015 constant price $US (gdp_const) 

NOTE: Canada is missing WB 2015 constant price US$ data points from 1990-1996, 
Canada's WB TS has been replaced with the OECD data
```{r}

dfi <- data %>% 
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2, 
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L), 
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>% 
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))
         
```

# Check difference in GDPs
```{r}

df %>% 
  filter(country %in% sel) %>% 
  ggplot() +
  geom_line(aes(x = year, y = lgdp), color = "blue") +
  geom_line(aes(x = year, y = lgdp_oecd), color = "red") +
  geom_line(aes(x = year, y = lgdp_wb), color = "black", linetype = "dashed") +
  facet_wrap(vars(country), scales = "free")
  
```


# Standard formula in log-levels and growth rates (fd logs)
Uses WB GDP data in this instance
```{r}

form <- c(
# Standard
"l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",

# Growth rates
"d.l_edgar_v7 ~ d.lgdp_wb + d.lpop + d.lgdp_wb_sq")

form_ets <- c(paste(form, "+ EU_ETS_05"),
              paste(form, "+ EU_ETS_08"), 
              paste(form, "+ EU_ETS_13"), 
              paste(form, "+ EU_ETS_05 + EU_ETS_08"),
              paste(form, "+ EU_ETS_05 + EU_ETS_13"),
              paste(form, "+ EU_ETS_08 + EU_ETS_13"),
              paste(form, "+ EU_ETS_05 + EU_ETS_08 + EU_ETS_13"))

```

# Standard log-level and growth rate formulas
504 models total
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

models <- foreach(f = c(form, form_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- df %>% 
    filter(country %in% sel & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = b
            )
          models = tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = b,
                          ar = a)
    }

saveRDS(models, here("output/final_results/standard_models.RDS"))

```

# Formulas with weather controls (IEA data: 2000:2021)
```{r}

form_weather <- c(
  # Integrating temperature controls (only valid for 2000:2021)
  "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + HDD16dailybypop + CDD18dailybypop",

  # Controlling only for population and temperature (removing GDP) (only valid for 2000:2021)
  "l_edgar_v7 ~ lpop + HDD16dailybypop + CDD18dailybypop"
)

form_ets_weather <- c(paste(form_weather, "+ EU_ETS_05"),
              paste(form_weather, "+ EU_ETS_08"), 
              paste(form_weather, "+ EU_ETS_13"), 
              paste(form_weather, "+ EU_ETS_05 + EU_ETS_08"),
              paste(form_weather, "+ EU_ETS_05 + EU_ETS_13"),
              paste(form_weather, "+ EU_ETS_08 + EU_ETS_13"),
              paste(form_weather, "+ EU_ETS_05 + EU_ETS_08 + EU_ETS_13"))

```

# Run weather controls
Restricted to 2000:2021 with IEA data
252 models
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

weather_models <- foreach(f = c(form_weather, form_ets_weather), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- df %>% 
    filter(country %in% sel & year >= 2000)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = b
            )
          models = tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = b,
                          ar = a)
    }

#saveRDS(weather_models, here("output/final_results/weather_models.RDS"))

```

# Formulas with weather controls from manually calculated population-weighted CDD and HDD
```{r}

df %>% filter(country %in% sel & year >= 1990) %>% select(year, country, HDD16dailybypop, CDD18dailybypop, hdd, cdd) %>% 
  pivot_longer(cols = !c(year, country), names_to = "cat", values_to = "n") %>% 
  ggplot(aes(x = year, y = n, color = cat)) +
  geom_line() +
  facet_wrap(vars(country), scales = "free")

form_dd <- c(
  # Integrating temperature controls (only valid for 2000:2021)
  "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd",

  # Controlling only for population and temperature (removing GDP) (only valid for 2000:2021)
  "l_edgar_v7 ~ lpop + hdd + cdd"
)

form_ets_dd <- c(paste(form_dd, "+ EU_ETS_05"),
              paste(form_dd, "+ EU_ETS_08"), 
              paste(form_dd, "+ EU_ETS_13"), 
              paste(form_dd, "+ EU_ETS_05 + EU_ETS_08"),
              paste(form_dd, "+ EU_ETS_05 + EU_ETS_13"),
              paste(form_dd, "+ EU_ETS_08 + EU_ETS_13"),
              paste(form_dd, "+ EU_ETS_05 + EU_ETS_08 + EU_ETS_13"))

```

# Run weather controls
Manually calculated CDD/HDD data
576 models
```{r}

cl <- makeCluster(7)
registerDoParallel(cl)

dd_calc_models <- foreach(f = c(form_dd, form_ets_dd), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- df %>% 
    filter(country %in% sel & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = b
            )
          models = tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = b,
                          ar = a)
    }

#saveRDS(dd_calc_models, here("output/final_results/weather_calc_dd_models.RDS"))

```


# Growth rates with higher p-value
12 models
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

gr_models <- foreach(a = c(0,1), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  foreach(b = c(10, 20, 30), .combine = rbind) %dopar% {
    dat <- df %>% 
    filter(country %in% sel & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = "d.l_edgar_v7 ~ d.lgdp_wb + d.lpop + d.lgdp_wb_sq",
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = 0.1,
            max.block.size = b
            )
          models = tibble(source = "d.l_edgar_v7 ~ d.lgdp_wb + d.lpop + d.lgdp_wb_sq", 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = 0.1, 
                          is = list(is),
                          iis = TRUE,
                          b_size = b,
                          ar = a)
  }

saveRDS(gr_models, here("output/final_results/growth_rate_high_pval.RDS"))

```



# TO BE ADDED: Growth rates with weather controls
```{r}


```

# Formulas in levels w/ temp controls and ETS dummies
```{r}
form_basic <- c(
# Standard
"l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",

"l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13")

```

# Run with standard 20 block size and no 5% sig value
```{r}

cfesis_models <- tibble()
for(f in form_basic){
  for(p.value in c(0.05, 0.01, 0.001)){
    dat <- df %>% 
    filter(country %in% sel & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            cfesis = TRUE,
            cfesis_var = c('lgdp_wb', 'lpop', 'lgdp_wb_sq'),
            #ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          cfesis_models <- rbind(cfesis_models, tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0))
    }
}
  #foreach(a = c(0,1), .combine = rbind) %:%
  #foreach(yr = c(1990, 2000), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    

cfesis_models %>% 
  mutate(cfesis = TRUE, cfesis_var = 'lgdp_wb;lpop;lgdp_wb_sq') %>% 
saveRDS(here("output/final_results/cfesis_models_Xtemp_XETS.RDS"))

```

# Run with standard 20 block size and no 5% sig value
```{r}

tis_test <- 
  for(p in c(0.05, 0.01, 0.001)){
    df %>%
    tis <- filter(country %in% sel & year >= 1990) %>% isatpanel(
            data = .,
            formula = "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            tis = TRUE,
            t.pval = p,
            max.block.size = 20
            )
  
  cfesis_models <- rbind(cfesis_models, tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(tis),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0))
```

# Common Correlated Effects CCE
```{r} 
##### Manually Implementing CCE Estimator
####create x-sectional averages
dat_simple <- df %>% filter(country %in% sel & year >= 1990) %>% select(country, year, l_edgar_v7, lgdp_wb, lpop, lgdp_wb_sq) %>% 
  group_by(year) %>% mutate(mean_l_emissions = mean(l_edgar_v7),
                            mean_lgdp = mean(lgdp_wb),
                            mean_lpop = mean(lpop),
                            mean_lgdp_sq = mean(lgdp_wb_sq)) %>% arrange(country)

# ### generate matrix of interactions so that each unit can have different coefficients
# Below to be automated

cce_dummies <- function(df, vars){
  vs <- list()
  for(v in vars){
    t <- as.matrix(df[[v]]*dummy_cols(df$country, remove_selected_columns = TRUE))
    colnames(t) = paste0(v, colnames(t))
    vs <- append(vs, list(t))
  } 
  names(vs) <- vars
  return(vs)
}

vt <- cce_dummies(dat_simple, c('mean_l_emissions', 'mean_lgdp', 'mean_lpop', 'mean_lgdp_sq'))

test_simple <- dat_simple %>% cbind(vt[[1]], vt[[2]], vt[[3]], vt[[4]]) %>% clean_names

# Note: automate column selection in formula for m1
m1 <- plm(as.formula(paste("l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + ", paste(names(test_simple[11:94]), collapse = "+"))) , data = test_simple, model="within", effect="twoways", index=c("country", "year"))
summary(m1)

m_pcce <- pcce(l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq, data = dat_simple, effect = "twoways", model="p", index=c("country", "year"))
summary(m_pcce)

for(i in 1:20){
  if(identical(round(m_pcce$coefficients, i), round(m1$coefficients[1:3], i))){
    next
  }else{
    print(paste("Coefficients identical at", i-1, "decimal places."))
    break}
}

#################################################################################
pcce_models <- tibble()
for(p.value in c(0.05, 0.01, 0.001)){
    is <- isatpanel(data = test_simple ,
            formula = as.formula(paste("l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + ", paste(names(test_simple[11:94]), collapse = "+"))),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = 20
            ) 
  pcce_models <- rbind(pcce_models, tibble(source = "pcce(l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq)", 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(test_simple$year),":",max(test_simple$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0))
}

saveRDS(pcce_models, here("output/final_results/pcce_models.RDS"))
# Wondering about user.estimator argument in isatpanel?
# calling plm engine automatically calls plm - any way to modify to call another function in plm package? ie. pcce

# Basic call from above: iis = TRUE, pval = 0.001, block size = 20
#saveRDS(t_pcce, here("output/pcce_trial2.RDS"))
# test2 <- readRDS(here("output/pcce_trial2.RDS"))
# 
# # Latest trial with updated variables: 
# # iis = TRUE, pval = 0.001, block size = 20
# 
# #saveRDS(t_pcce, here("output/pcce_trial.RDS"))
# saveRDS(t_pcce001, here("output/pcce_trial001.RDS"))
# saveRDS(t_pcce05, here("output/pcce_trial05.RDS"))
# saveRDS(t_pcce01, here("output/pcce_trial01.RDS"))
# test <- readRDS(here("output/pcce_trial.RDS"))
