---
title: "Full_Analysis"
author: "Ebba Mark"
date: "`r Sys.Date()`"
output: html_document
---

# Load libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())
library(data.table)
library(tidyverse)
library(openxlsx)
library(stringr)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(fastDummies)
library(janitor)
library(plm)
# 
# install.packages(
#   "https://github.com/gsucarrat/gets/raw/master/gets_devel.tar.gz",
#   repos = NULL, type = "source"
# )

#devtools::install_github("moritzpschwarz/getspanel")

source(here("code/dicts.R"))

data <- readRDS(here("data/out/elec_emissions_panel_clean_22.RDS"))

```

# Create controls, scale emissions (ktco2/ktco2e), other required transformations (FD, lags, growth rates)
# 28/10: GDP (current US$) replaced with GDP (constant 2015 $US)

Three available GDP indicators: 
- WB GDP current US$ (gdp)   
- OECD 2015 constant prices US$ (gdp_const_oecd)   
- WB 2015 constant price $US (gdp_const) 

NOTE: Canada is missing WB 2015 constant price US$ data points from 1990-1996, 
Canada's WB TS has been replaced with the OECD data
```{r}

dfi <- data %>% 
  mutate(gdp_sq = gdp^2,
         gdp_wb_sq = gdp_const^2,
         gdp_oecd_sq = gdp_const_oecd^2,
         lpop = log(pop),
         lgdp = log(gdp),
         lgdp_wb = log(gdp_const),
         lgdp_oecd = log(gdp_const_oecd),
         lgdp_sq = log(gdp)^2,
         lgdp_wb_sq = log(gdp_const)^2,
         lgdp_oecd_sq = log(gdp_const_oecd)^2, 
         edgar_v7_elec_ktco2 = edgar_v7_elec_mtco2*1000,
         l_edgar_v7 = log(edgar_v7_elec_ktco2),
         owid_1_elec_heat_ktco2e = owid_1_elec_heat_tco2e/1000,
         owid_2_elec_ktco2e = owid_2_elec_mtco2e*1000,
         bp_energy_ktco2 = bp_energy_mtco2*1000)

df <- dfi %>% group_by(country) %>%
  # Lags (3), first-difference (growth rate = fd in log) (EDGAR V7), lgdp (WB current, WB constant 2015, OECD constant 2015), lpop, lgdp_sq (WB current, WB constant 2015, OECD constant 2015)
  mutate(across(c(l_edgar_v7, lgdp, lgdp_wb, lgdp_oecd, lpop, lgdp_sq, lgdp_wb_sq, lgdp_oecd_sq), list(l1 = ~lag(.x, n = 1L),
         l2 = ~lag(.x, n = 2L),
         l3 = ~lag(.x, n = 3L), 
         d = ~c(NA, diff(.x, differences = 1))),
          #g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))*100),
         .names = "{.fn}.{.col}")) %>% 
  mutate(EU_ETS_05 = ifelse(country %in% EU15 & year >= 2005, 1, 0),
         EU_ETS_08 = ifelse(country %in% EU15 & year >= 2008, 1, 0),
         EU_ETS_13 = ifelse(country %in% EU15 & year >= 2013, 1, 0))
         
```

# Check difference in GDPs
```{r}

df %>% 
  filter(country %in% sel) %>% 
  ggplot() +
  geom_line(aes(x = year, y = lgdp), color = "blue", na.rm = TRUE) +
  geom_line(aes(x = year, y = lgdp_oecd), color = "red", na.rm = TRUE) +
  geom_line(aes(x = year, y = lgdp_wb), color = "black", linetype = "dashed", na.rm = TRUE) +
  facet_wrap(vars(country), scales = "free")
  
```


# Standard formula in log-levels and growth rates (fd logs)
Uses WB GDP data in this instance
```{r}

form <- c(
# Standard
"l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",

# Growth rates
"d.l_edgar_v7 ~ d.lgdp_wb + d.lpop + d.lgdp_wb_sq")

form_ets <- c(paste(form, "+ EU_ETS_05"),
              paste(form, "+ EU_ETS_08"), 
              paste(form, "+ EU_ETS_13"), 
              paste(form, "+ EU_ETS_05 + EU_ETS_08"),
              paste(form, "+ EU_ETS_05 + EU_ETS_13"),
              paste(form, "+ EU_ETS_08 + EU_ETS_13"),
              paste(form, "+ EU_ETS_05 + EU_ETS_08 + EU_ETS_13"))

```

# Standard log-level and growth rate formulas
504 models total
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

models <- foreach(f = c(form, form_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- df %>% 
    filter(country %in% sel & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = b
            )
          models = tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = b,
                          ar = a)
    }

saveRDS(models, here("output/final_results/standard_models.RDS"))

```

# EXCLUDE: Formulas with weather controls (IEA data: 2000:2021)
```{r}

form_weather <- c(
  # Integrating temperature controls (only valid for 2000:2021)
  "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + HDD16dailybypop + CDD18dailybypop",

  # Controlling only for population and temperature (removing GDP) (only valid for 2000:2021)
  "l_edgar_v7 ~ lpop + HDD16dailybypop + CDD18dailybypop"
)

form_ets_weather <- c(paste(form_weather, "+ EU_ETS_05"),
              paste(form_weather, "+ EU_ETS_08"), 
              paste(form_weather, "+ EU_ETS_13"), 
              paste(form_weather, "+ EU_ETS_05 + EU_ETS_08"),
              paste(form_weather, "+ EU_ETS_05 + EU_ETS_13"),
              paste(form_weather, "+ EU_ETS_08 + EU_ETS_13"),
              paste(form_weather, "+ EU_ETS_05 + EU_ETS_08 + EU_ETS_13"))

```

# Run weather controls
Restricted to 2000:2021 with IEA data
252 models
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

weather_models <- foreach(f = c(form_weather, form_ets_weather), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- df %>% 
    filter(country %in% sel & year >= 2000)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = b
            )
          models = tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = b,
                          ar = a)
    }

#saveRDS(weather_models, here("output/final_results/weather_models.RDS"))

```

# Formulas with weather controls from manually calculated population-weighted CDD and HDD
```{r}

df %>% filter(country %in% sel & year >= 1990) %>% select(year, country, HDD16dailybypop, CDD18dailybypop, hdd, cdd) %>% 
  pivot_longer(cols = !c(year, country), names_to = "cat", values_to = "n") %>% 
  ggplot(aes(x = year, y = n, color = cat)) +
  geom_line(na.rm = TRUE) +
  facet_wrap(vars(country), scales = "free")

form_dd <- c(
  # Integrating temperature controls (only valid for 2000:2021)
  "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd",

  # Controlling only for population and temperature (removing GDP) (only valid for 2000:2021)
  "l_edgar_v7 ~ lpop + hdd + cdd"
)

form_ets_dd <- c(paste(form_dd, "+ EU_ETS_05"),
              paste(form_dd, "+ EU_ETS_08"), 
              paste(form_dd, "+ EU_ETS_13"), 
              paste(form_dd, "+ EU_ETS_05 + EU_ETS_08"),
              paste(form_dd, "+ EU_ETS_05 + EU_ETS_13"),
              paste(form_dd, "+ EU_ETS_08 + EU_ETS_13"),
              paste(form_dd, "+ EU_ETS_05 + EU_ETS_08 + EU_ETS_13"))

```

# Run weather controls
Manually calculated CDD/HDD data
576 models
```{r}

cl <- makeCluster(7)
registerDoParallel(cl)

dd_calc_models <- foreach(f = c(form_dd, form_ets_dd), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- df %>% 
    filter(country %in% sel & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = b
            )
          models = tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = b,
                          ar = a)
    }

#saveRDS(dd_calc_models, here("output/final_results/weather_calc_dd_models.RDS"))

```


# Growth rates with higher p-value
12 models
```{r}

cl <- makeCluster(6)
registerDoParallel(cl)

gr_models <- foreach(a = c(0,1), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  foreach(b = c(10, 20, 30), .combine = rbind) %dopar% {
    dat <- df %>% 
    filter(country %in% sel & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = "d.l_edgar_v7 ~ d.lgdp_wb + d.lpop + d.lgdp_wb_sq",
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = 0.1,
            max.block.size = b
            )
          models = tibble(source = "d.l_edgar_v7 ~ d.lgdp_wb + d.lpop + d.lgdp_wb_sq", 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = 0.1, 
                          is = list(is),
                          iis = TRUE,
                          b_size = b,
                          ar = a)
  }

#saveRDS(gr_models, here("output/final_results/growth_rate_high_pval.RDS"))

```

# Formulas in levels w/ temp controls and ETS dummies
```{r}
form_basic <- c(
# Standard
"l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",

"l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13")

```

# Run with standard 20 block size and no 5% sig value
```{r}

cfesis_models <- tibble()
for(f in form_basic){
  for(p.value in c(0.05, 0.01, 0.001)){
    dat <- df %>% 
    filter(country %in% sel & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            cfesis = TRUE,
            cfesis_var = c('lgdp_wb', 'lpop', 'lgdp_wb_sq'),
            #ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          cfesis_models <- rbind(cfesis_models, tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0))
    }
}
  #foreach(a = c(0,1), .combine = rbind) %:%
  #foreach(yr = c(1990, 2000), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    

cfesis_models %>% 
  mutate(cfesis = TRUE, cfesis_var = 'lgdp_wb;lpop;lgdp_wb_sq') %>% 
saveRDS(here("output/final_results/cfesis_models_Xtemp_XETS.RDS"))

```

# Run with standard 20 block size and no 5% sig value
```{r}

tis_test <- 
  for(p in c(0.05, 0.01, 0.001)){
    df %>%
    tis <- filter(country %in% sel & year >= 1990) %>% isatpanel(
            data = .,
            formula = "l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq",
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            tis = TRUE,
            t.pval = p,
            max.block.size = 20
            )
  
  cfesis_models <- rbind(cfesis_models, tibble(source = f, 
                          country_sample = "EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(tis),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0))
```

# Selected sample WITHOUT LUXEMBOURG
```{r}

form_b <- c(form[1], form_dd)

form_b_ets <- c(form_b, 
                paste(form_b, "+ EU_ETS_05 + EU_ETS_08 + EU_ETS_13"))


form_b_ets_add <- c(paste(form_b, "+ EU_ETS_05"),
              paste(form_b, "+ EU_ETS_08"), 
              paste(form_b, "+ EU_ETS_13"), 
              paste(form_b, "+ EU_ETS_05 + EU_ETS_08"),
              paste(form_b, "+ EU_ETS_05 + EU_ETS_13"),
              paste(form_b, "+ EU_ETS_08 + EU_ETS_13"))

cl <- makeCluster(6)
registerDoParallel(cl)

# m_nolux <- foreach(f = c(form_b_ets), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
#   foreach(a = c(0,1), .combine = rbind) %:%
#   foreach(yr = c(1990, 2000), .combine = rbind) %:%
#   #foreach(b = c(10, 20, 30), .combine = rbind) %:%
#     foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
#     dat <- df %>% 
#     filter(country %in% sel[sel != "Luxembourg"] & year >= yr)
#       is <- isatpanel(
#             data = dat,
#             formula = as.formula(f),
#             index = c("country", "year"),
#             effect = "twoways",
#             iis = TRUE,
#             fesis = TRUE,
#             ar = a,
#             t.pval = p.value,
#             max.block.size = b
#             )
#           models = tibble(source = f, 
#                           country_sample = "NOLUX_EU15+selected", 
#                           year_range = paste0(min(dat$year),":",max(dat$year)), 
#                           p_val = p.value, 
#                           is = list(is),
#                           iis = TRUE,
#                           b_size = b,
#                           ar = a)
#     }


# Run more ETS specs
m_nolux_addets <- foreach(f = c(form_b_ets_add), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- df %>%
    filter(country %in% sel[sel != "Luxembourg"] & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
    }


#saveRDS(m_nolux, here("output/temp/nolux_simpleets.RDS"))
#saveRDS(m_nolux_bs, here("output/temp/nolux_simpleets_bs10_30.RDS"))
#saveRDS(m_nolux_addets, here("output/temp/nolux_further_ets_20.RDS"))

m_nolux_addets %>% pull(is) %>% first %>% plot

#saveRDS(models, here("output/final_results/standard_models.RDS"))

```


# Growth rates without Luxembourg
12 models
```{r}

df2 <- df %>% 
  filter(country %in% sel & year >= 1989) %>% 
  group_by(country) %>%
  mutate(across(c(cdd, hdd), list(
    d = ~c(NA, diff(.x, differences = 1)),
    g = ~(c(NA, diff(.x, differences = 1))/lag(.x, n = 1L))),
         .names = "{.fn}.{.col}")) %>% 
  mutate(g.cdd = ifelse(d.cdd == 0 | g.cdd == Inf, 0, g.cdd))

gr_forms <- c(
  # "d.l_edgar_v7 ~ d.lgdp_wb + d.lpop + d.lgdp_wb_sq",
  "d.l_edgar_v7 ~ d.lgdp_wb + d.lpop + d.lgdp_wb_sq + g.cdd + g.hdd",
  "d.l_edgar_v7 ~ d.lpop + g.cdd + g.hdd")

cl <- makeCluster(6)
registerDoParallel(cl)
gr_nolux_alts <- foreach(f = c(gr_forms), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
   foreach(a = c(0,1), .combine = rbind) %:%
   foreach(p.value = c(0.1, 0.05, 0.01, 0.001), .combine = rbind) %dopar% {
  #foreach(b = c(10, 20, 30), .combine = rbind) 
    dat <- df2 %>% 
    filter(country %in% sel[sel != "Luxembourg"] & year >= 1990)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = a,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected", 
                          year_range = paste0(min(dat$year),":",max(dat$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = a)
  }

saveRDS(gr_nolux_alts, here("output/temp/growth_rate_temp_nolux.RDS"))

```


# CCE: Standard
```{r} 
##### Manually Implementing CCE Estimator
####create x-sectional averages
dat_simple <- df %>% filter(country %in% sel[sel != "Luxembourg"] & year >= 1990) %>% select(country, year, l_edgar_v7, lgdp_wb, lpop, lgdp_wb_sq) %>% 
  group_by(year) %>% mutate(mean_l_emissions = mean(l_edgar_v7),
                            mean_lgdp = mean(lgdp_wb),
                            mean_lpop = mean(lpop),
                            mean_lgdp_sq = mean(lgdp_wb_sq)) %>% arrange(country)

# ### generate matrix of interactions so that each unit can have different coefficients
# Below to be automated

cce_dummies <- function(df, vars){
  vs <- list()
  for(v in vars){
    t <- as.matrix(df[[v]]*dummy_cols(df$country, remove_selected_columns = TRUE))
    colnames(t) = paste0(v, colnames(t))
    vs <- append(vs, list(t))
  } 
  names(vs) <- vars
  return(vs)
}

vt <- cce_dummies(dat_simple, c('mean_l_emissions', 'mean_lgdp', 'mean_lpop', 'mean_lgdp_sq'))

test_simple <- dat_simple %>% cbind(vt[[1]], vt[[2]], vt[[3]], vt[[4]]) %>% clean_names

# Note: automate column selection in formula for m1
m1 <- plm(as.formula(paste("l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + ", paste(names(test_simple[11:90]), collapse = "+"))) , data = test_simple, model="within", effect="individual", index=c("country", "year"))
summary(m1)

m_pcce <- pcce(l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq, data = dat_simple, model="p", effect = "individual", index=c("country", "year"))
summary(m_pcce)

for(i in 1:20){
  if(identical(round(m_pcce$coefficients, i), round(m1$coefficients[1:3], i))){
    next
  }else{
    print(paste("Coefficients identical at", i-1, "decimal places."))
    break}
}

#################################################################################
pcce_models <- tibble()
for(p.value in c(0.05, 0.01, 0.001)){
    is <- isatpanel(data = test_simple ,
            formula = as.formula(paste("l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + ", paste(names(test_simple[11:90]), collapse = "+"))),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = 20
            ) 
  pcce_models <- rbind(pcce_models, tibble(source = "pcce(l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq)", 
                          country_sample = "NOLUXEU15+selected", 
                          year_range = paste0(min(test_simple$year),":",max(test_simple$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0))
}

saveRDS(pcce_models, here("output/final_results/pcce_models_twfeffects_nolux.RDS"))
# Wondering about user.estimator argument in isatpanel?
# calling plm engine automatically calls plm - any way to modify to call another function in plm package? ie. pcce

# Basic call from above: iis = TRUE, pval = 0.001, block size = 20
#saveRDS(t_pcce, here("output/pcce_trial2.RDS"))
# test2 <- readRDS(here("output/pcce_trial2.RDS"))
# 
# # Latest trial with updated variables: 
# # iis = TRUE, pval = 0.001, block size = 20
# 
# saveRDS(t_pcce, here("output/pcce_trial.RDS"))
# saveRDS(t_pcce001, here("output/pcce_trial001.RDS"))
# saveRDS(t_pcce05, here("output/pcce_trial05.RDS"))
# saveRDS(t_pcce01, here("output/pcce_trial01.RDS"))

```

# CCE: Standard with Temp
```{r} 
##### Manually Implementing CCE Estimator
####create x-sectional averages
dat_simple <- df %>% filter(country %in% sel[sel != "Luxembourg"] & year >= 1990) %>% select(country, year, l_edgar_v7, lgdp_wb, lpop, lgdp_wb_sq, cdd, hdd) %>% 
  group_by(year) %>% mutate(mean_l_emissions = mean(l_edgar_v7),
                            mean_lgdp = mean(lgdp_wb),
                            mean_lpop = mean(lpop),
                            mean_lgdp_sq = mean(lgdp_wb_sq),
                            mean_cdd = mean(cdd),
                            mean_hdd = mean(hdd)) %>% arrange(country)

# ### generate matrix of interactions so that each unit can have different coefficients
# Below to be automated

cce_dummies <- function(df, vars){
  vs <- list()
  for(v in vars){
    t <- as.matrix(df[[v]]*dummy_cols(df$country, remove_selected_columns = TRUE))
    colnames(t) = paste0(v, colnames(t))
    vs <- append(vs, list(t))
  } 
  names(vs) <- vars
  return(vs)
}

vt <- cce_dummies(dat_simple, c('mean_l_emissions', 'mean_lgdp', 'mean_lpop', 'mean_lgdp_sq'))

test_simple <- dat_simple %>% cbind(vt[[1]], vt[[2]], vt[[3]], vt[[4]]) %>% clean_names

# Note: automate column selection in formula for m1
m1 <- plm(as.formula(paste("l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + ", paste(names(test_simple[11:90]), collapse = "+"))) , data = test_simple, model="within", effect="individual", index=c("country", "year"))
summary(m1)

m_pcce <- pcce(l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq, data = dat_simple, model="p", effect = "individual", index=c("country", "year"))
summary(m_pcce)

for(i in 1:20){
  if(identical(round(m_pcce$coefficients, i), round(m1$coefficients[1:3], i))){
    next
  }else{
    print(paste("Coefficients identical at", i-1, "decimal places."))
    break}
}

#################################################################################
pcce_models <- tibble()
for(p.value in c(0.05, 0.01, 0.001)){
    is <- isatpanel(data = test_simple ,
            formula = as.formula(paste("l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq + ", paste(names(test_simple[11:90]), collapse = "+"))),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            t.pval = p.value,
            max.block.size = 20
            ) 
  pcce_models <- rbind(pcce_models, tibble(source = "pcce(l_edgar_v7 ~ lgdp_wb + lpop + lgdp_wb_sq)", 
                          country_sample = "NOLUXEU15+selected", 
                          year_range = paste0(min(test_simple$year),":",max(test_simple$year)), 
                          p_val = p.value, 
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0))
}

saveRDS(pcce_models, here("output/final_results/pcce_models_twfeffects_nolux.RDS"))
# Wondering about user.estimator argument in isatpanel?
# calling plm engine automatically calls plm - any way to modify to call another function in plm package? ie. pcce

# Basic call from above: iis = TRUE, pval = 0.001, block size = 20
#saveRDS(t_pcce, here("output/pcce_trial2.RDS"))
# test2 <- readRDS(here("output/pcce_trial2.RDS"))
# 
# # Latest trial with updated variables: 
# # iis = TRUE, pval = 0.001, block size = 20
# 
# saveRDS(t_pcce, here("output/pcce_trial.RDS"))
# saveRDS(t_pcce001, here("output/pcce_trial001.RDS"))
# saveRDS(t_pcce05, here("output/pcce_trial05.RDS"))
# saveRDS(t_pcce01, here("output/pcce_trial01.RDS"))

```

# Energy shares
Share of electricity generation per fuel type
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review

```{r} 

shares_df <- 
  df %>%
  mutate(fossil_share_elec = ifelse(is.na(fossil_share_elec), 100 - low_carbon_share_elec, fossil_share_elec)) %>%
  filter(country %in% sel & year >=1990) %>% 
  select(country, year, ets_price,
         l_edgar_v7,
         lgdp_wb, lgdp_wb_sq, lpop, EU_ETS_05, EU_ETS_08, EU_ETS_13, hdd, cdd,
         low_carbon_share_elec,
         renewables_share_elec,
         other_renewables_share_elec,
         other_renewables_share_elec_exc_biofuel,
         biofuel_share_elec,
         fossil_share_elec,
         coal_share_elec,
         oil_share_elec,
         gas_share_elec,
         nuclear_share_elec,
         solar_share_elec,
         wind_share_elec,
         hydro_share_elec,
         contains("_electricity"),
         -per_capita_electricity
         )

share_controls <- c("~ lgdp_wb + lpop + lgdp_wb_sq",
                 "~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd",
                 "~ lpop + hdd + cdd",
                 "~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13",
                 "~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13",
                 "~ lpop + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13")

share_forms <- c(paste("low_carbon_share_elec", share_controls),
                       paste("renewables_share_elec", share_controls),
                             paste("fossil_share_elec", share_controls))

source_forms <- c(paste("solar_share_elec", share_controls),
                  paste("hydro_share_elec", share_controls),
                  paste("wind_share_elec", share_controls),
                  paste("nuclear_share_elec", share_controls),
                  paste("oil_share_elec", share_controls),
                  paste("coal_share_elec", share_controls),
                  paste("gas_share_elec", share_controls))

cl <- makeCluster(6)
registerDoParallel(cl)

shares_sources <- foreach(f = c(source_forms), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  #foreach(a = c(0,1), .combine = rbind) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- shares_df %>%
    filter(country %in% sel & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = 0,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0)
    }

#saveRDS(shares_sources_nolux, here("output/temp/shares_bysource_noar_nolux.RDS"))
saveRDS(shares_sources, here("output/temp/shares_bysource_noar.RDS"))

```

# Interact ETS dummy with price
```{r}

ets_price_covs <- c("~ lgdp_wb + lpop + lgdp_wb_sq + EU_ETS_05 + EU_ETS_08 + EU_ETS_13 + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price",
                 "~ lgdp_wb + lpop + lgdp_wb_sq + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13 + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price",
                 "~ lpop + hdd + cdd + EU_ETS_05 + EU_ETS_08 + EU_ETS_13 + EU_ETS_05:ets_price + EU_ETS_08:ets_price + EU_ETS_13:ets_price")

forms_ets_price <- c(paste("l_edgar_v7", ets_price_covs),
                 paste("low_carbon_share_elec", ets_price_covs),
                 paste("renewables_share_elec", ets_price_covs),
                 paste("fossil_share_elec", ets_price_covs),
                 paste("solar_share_elec", ets_price_covs),
                 paste("hydro_share_elec", ets_price_covs),
                 paste("wind_share_elec", ets_price_covs),
                 paste("nuclear_share_elec", ets_price_covs),
                 paste("oil_share_elec", ets_price_covs),
                 paste("coal_share_elec", ets_price_covs),
                 paste("gas_share_elec", ets_price_covs))

cl <- makeCluster(7)
registerDoParallel(cl)

temp_ets_prices <- foreach(f = c(forms_ets_price), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  foreach(a = c(0,1), .combine = rbind) %:%
   #foreach(b = c(10, 20, 30), .combine = rbind) %:%
     foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
     dat <- df %>%
     filter(country %in% sel[sel != "Luxembourg"] & year >= 1990) %>% 
       mutate(ets_price = ifelse(year < 2005, 0, ets_price))
       is <- isatpanel(
            data = dat,
             formula = as.formula(f),
             index = c("country", "year"),
             effect = "twoways",
             iis = TRUE,
             fesis = TRUE,
             ar = a,
             t.pval = p.value,
             max.block.size = 20
             )
           temp_ets_prices = tibble(source = f,
                           country_sample = "NOLUX_EU15+selected",
                           year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                           is = list(is),
                           iis = TRUE,
                           b_size = 20,
                          ar = a)
     }

saveRDS(temp_ets_prices, here("output/temp/mod_ets_price.RDS"))

#saveRDS(shares_ets, here("output/temp/shares_ets_noar.RDS"))
saveRDS(temporary_ets_shares, here("output/temp/temporary_ets_shares.RDS"))
```



# Electricity generation per source (TWH)
Additional option: Electricity generation per fuel type, measured in terawatt-hours
Source: OWID via BP Statistical Review of World Energy and Ember Global and European Electricity Review
```{r}

df %>% 
  select(country, year, low_carbon_electricity, renewables_electricity, fossil_electricity) %>% 
  filter(country %in% sel & year >=2020) %>% 
  pivot_longer(!c(country, year), names_to = 'source', values_to = 'elect_twh') %>%
  ggplot(aes(x = year, y = elect_twh, color = source)) +
  geom_line(na.rm = TRUE) +
  facet_wrap(~country, scales = "free")

# Run more ETS specs
m_nolux_addets <- foreach(f = c(form_b_ets_add), .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:%
  #foreach(a = c(0,1), .combine = rbind) %:%
  foreach(yr = c(1990, 2000), .combine = rbind) %:%
  #foreach(b = c(10, 20, 30), .combine = rbind) %:%
    foreach(p.value = c(0.05, 0.01, 0.001), .combine = rbind) %dopar% {
    dat <- df %>%
    filter(country %in% sel[sel != "Luxembourg"] & year >= yr)
      is <- isatpanel(
            data = dat,
            formula = as.formula(f),
            index = c("country", "year"),
            effect = "twoways",
            iis = TRUE,
            fesis = TRUE,
            ar = 0,
            t.pval = p.value,
            max.block.size = 20
            )
          models = tibble(source = f,
                          country_sample = "NOLUX_EU15+selected",
                          year_range = paste0(min(dat$year),":",max(dat$year)),
                          p_val = p.value,
                          is = list(is),
                          iis = TRUE,
                          b_size = 20,
                          ar = 0)
    }

```

